---
title: "PhD Chapter 1 - PatchSize"
author: "Emanuele Giacomuzzo"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
bibliography: library.bib
html_document:
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
    includes:
      after_body: tabset-dropdown.html
editor_options: 
  chunk_output_type: console
---

#  {.tabset}

```{r echo=FALSE, message=FALSE}
start_time = Sys.time()
library("here")
```

```{r child = here("r_files", "packages.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "functions.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "parameters.Rmd"), echo = FALSE}
```

## Overview {.tabset .tabset-pills}

```{r overview-experiment, child = here("r_files", "overview.Rmd"), eval = compute_n_display_datasets}
```

## Data {.tabset .tabset-dropdown}

### Experimental cultures (`culture_info`)

```{r child = here("r_files", "ds_culture_info.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_patches.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_patches_effect_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_metaecosystems.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_individuals.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_median_body_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_median_body_size_effect_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_classes.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "ds_classes_effect_size.Rmd"), eval = compute_n_display_datasets}
```

### Filter according to disturbance

```{r child = here("r_files", "disturbance_filter.Rmd")}
```

## Meta-ecosystems {.tabset .tabset-dropdown}

### All {.tabset .tabset-pills}

```{r}
metaecosystem_type_input = c("Small-Small meta-ecosystem",
                             "Medium-Medium meta-ecosystem",
                             "Medium-Medium isolated",
                             "Large-Large meta-ecosystem",
                             "Small-Large meta-ecosystem",
                             "Small-Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_biomass.Rmd")}
```

#### Alpha {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_alpha_diversity.Rmd")}
```

#### Beta diversity {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_beta_diversity.Rmd")}
```

#### Gamma diversity {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_gamma_diversity.Rmd")}
```

### MM vs SL (meta-ecosystems and isolated) {.tabset .tabset-pills}

```{r}
metaecosystem_type_input = c("Medium-Medium meta-ecosystem",
                             "Medium-Medium isolated",
                             "Small-Large meta-ecosystem",
                             "Small-Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_biomass.Rmd")}
```

#### Alpha diversity {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_alpha_diversity.Rmd")}
```

#### Beta diversity {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_beta_diversity.Rmd")}
```

#### Gamma diversity {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_gamma_diversity.Rmd")}
```

## Patches {.tabset .tabset-dropdown}

### Isolated {.tabset .tabset-pills}

```{r}
eco_metaeco_type_input = c("Small isolated",
                           "Medium isolated",
                           "Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_biomass.Rmd")}
```

#### Shannon index {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_alpha_diversity.Rmd")}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_evenness.Rmd")}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_densities.Rmd")}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_dominance.Rmd")}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_composition.Rmd")}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_size_classes.Rmd")}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_median_body_size.Rmd")}
```

### Small {.tabset .tabset-pills}

```{r}
eco_metaeco_type_input = c("Small isolated",
                           "Small connected to small",
                           "Small connected to large")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_biomass.Rmd")}
```

#### Shannon index {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_alpha_diversity.Rmd")}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_evenness.Rmd")}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_densities.Rmd")}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_dominance.Rmd")}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_composition.Rmd")}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_size_classes.Rmd")}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_median_body_size.Rmd")}
```

### Medium {.tabset .tabset-pills}

```{r}
eco_metaeco_type_input = c("Medium isolated",
                           "Medium connected to medium")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "medium_patches_biomass.Rmd")}
```

### Large {.tabset .tabset-pills}

```{r}
eco_metaeco_type_input = c("Large isolated",
                           "Large connected to large",
                           "Large connected to small")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_biomass.Rmd")}
```

#### Shannon index {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_alpha_diversity.Rmd")}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_evenness.Rmd")}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_densities.Rmd")}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_dominance.Rmd")}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_composition.Rmd")}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_size_classes.Rmd")}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_median_body_size.Rmd")}
```

### SL {.tabset .tabset-pills}

```{r}
eco_metaeco_type_input = c("Small connected to large",
                           "Large connected to small")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "SL_biomass.Rmd")}
```

#### Alpha diversity {.tabset .tabset-pills}

```{r child = here("r_files", "SL_alpha_diversity.Rmd")}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "SL_evenness.Rmd")}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_densities.Rmd")}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_dominance.Rmd")}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_composition.Rmd")}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "SL_size_classes.Rmd")}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "SL_median_body_size.Rmd")}
```

## Productivity drivers {.tabset .tabset-pills}

```{r child = here("r_files", "relationship_productivity_richness.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_shannon.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_evenness.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_dominance.Rmd")}
```

## Evaporation {.tabset .tabset-dropdown}

```{r child = here("r_files", "evaporation.Rmd"), eval = FALSE}
```

```{r child = here("r_files", "evaporation_tests.Rmd")}
```

## Video analysis script

```{r child = here("r_files", "video_analysis_script.Rmd"), class.source = "fold-show"}
```

## Paper

```{r child = here("r_files", "paper.Rmd")}
```

## Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time
```

## Other

In the .bib file get rid of:

-   book_section

-   computer_program

-   web_page

## Bibliography

```{r echo=FALSE, message=FALSE}
save.image(file = "my_environment.RData")
```

