---
title: "PhD Chapter 1 - PatchSize"
author: "Emanuele Giacomuzzo"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
    profiling: true
bibliography: library.bib
html_document:
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
    includes:
      after_body: tabset-dropdown.html
editor_options: 
  chunk_output_type: console
---

```{r echo=FALSE, results = FALSE, message = FALSE}
knitr::opts_chunk$set(message = FALSE,
                      cache = FALSE,
                      autodep = FALSE)

start_time = Sys.time()

library("here")

show_results = TRUE
recompute_analyses = FALSE #Lengthy analyses have been suppressed. Set recompute_analyses = TRUE to redo them.
control = FALSE
disturbance_input = "low"

print(paste("!!", disturbance_input, "!!", "(this document showcases only the analysis done for the", disturbance_input, "disturbance)"))
```

#  {.tabset}

```{r child = here("r_files", "packages.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "functions.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "parameters.Rmd"), echo = FALSE}
```

## Overview {.tabset .tabset-pills}

```{r overview-experiment, child = here("r_files", "overview.Rmd")}
```

## Data {.tabset .tabset-dropdown}

### Experimental cultures (`culture_info`)

```{r child = here("r_files", "ds_culture_info.Rmd")}
```

### Patches (`ds_patches`)

```{r child = here("r_files", "ds_patches.Rmd")}
```

### Patch effect sizes (`ds_patches_effect_size`)

```{r child = here("r_files", "ds_patches_effect_size.Rmd")}
```

### Meta-ecosystems (`ds_metaecosystems`)

```{r child = here("r_files", "ds_metaecosystems.Rmd")}
```

### Individuals (ds_individuals)

```{r child = here("r_files", "ds_individuals.Rmd")}
```

### Median body size (`ds_median_body_size)`

```{r child = here("r_files", "ds_median_body_size.Rmd")}
```

### Median body size effect size (`ds_median_body_size_effect_size`)

```{r child = here("r_files", "ds_median_body_size_effect_size.Rmd")}
```

### Size classes (`ds_classes`)

```{r child = here("r_files", "ds_classes.Rmd")}
```

### Size classes effect size (`ds_classes_effect_size`)

```{r child = here("r_files", "ds_classes_effect_size.Rmd")}
```

### Filter according to disturbance

```{r child = here("r_files", "disturbance_filter.Rmd")}
```

## Meta-ecosystems {.tabset .tabset-pills}

### All {.tabset .tabset-dropdown}

```{r}
metaecosystem_type_input = c("Small-Small meta-ecosystem",
                             "Medium-Medium meta-ecosystem",
                             "Medium-Medium isolated",
                             "Large-Large meta-ecosystem",
                             "Small-Large meta-ecosystem",
                             "Small-Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_alpha_diversity.Rmd"), eval = show_results}
```

#### Beta diversity {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_beta_diversity.Rmd"), eval = show_results}
```

#### Gamma diversity {.tabset .tabset-pills}

```{r child = here("r_files", "all_metaecos_gamma_diversity.Rmd"), eval = show_results}
```

### MM vs SL (meta-ecosystems and isolated) {.tabset .tabset-dropdown}

```{r}
metaecosystem_type_input = c("Medium-Medium meta-ecosystem",
                             "Medium-Medium isolated",
                             "Small-Large meta-ecosystem",
                             "Small-Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_alpha_diversity.Rmd"), eval = show_results}
```

#### Beta diversity {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_beta_diversity.Rmd"), eval = show_results}
```

#### Gamma diversity {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_gamma_diversity.Rmd"), eval = show_results}
```

## Patches {.tabset .tabset-pills}

### All {.tabset .tabset-dropdown}

```{r child = here("r_files", "all_patches_BEF.Rmd"), eval = show_results}
```

### Isolated {.tabset .tabset-dropdown}

```{r}
patch_type_input = c("Small isolated",
                     "Medium isolated",
                     "Large isolated")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_alpha_diversity.Rmd"), eval = show_results}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_evenness.Rmd"), eval = show_results}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_densities.Rmd"), eval = show_results}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_dominance.Rmd"), eval = show_results}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_species_composition.Rmd"), eval = show_results}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_size_classes.Rmd"), eval = show_results}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_median_body_size.Rmd"), eval = show_results}
```

### Small {.tabset .tabset-dropdown}

```{r}
patch_type_input = c("Small isolated",
                     "Small connected to small",
                     "Small connected to large")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_alpha_diversity.Rmd"), eval = show_results}
```

#### Alpha diversity (Species richness) {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_richness.Rmd"), eval = show_results}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_evenness.Rmd"), eval = show_results}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_densities.Rmd"), eval = show_results}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_dominance.Rmd"), eval = show_results}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_species_composition.Rmd"), eval = show_results}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_size_classes.Rmd"), eval = show_results}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_median_body_size.Rmd"), eval = show_results}
```

### Medium {.tabset .tabset-dropdown}

```{r}
patch_type_input = c("Medium isolated",
                     "Medium connected to medium")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "medium_patches_biomass.Rmd"), eval = show_results}
```

### Large {.tabset .tabset-dropdown}

```{r}
patch_type_input = c("Large isolated",
                     "Large connected to large",
                     "Large connected to small")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_alpha_diversity.Rmd"), eval = show_results}
```

#### Alpha diversity (Species richness) {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_richness.Rmd"), eval = show_results}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_evenness.Rmd"), eval = show_results}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_densities.Rmd"), eval = show_results}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_dominance.Rmd"), eval = show_results}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_species_composition.Rmd"), eval = show_results}
```

#### Community divergence from isolated

```{r child = here("r_files", "large_community_divergence_from_isolated.Rmd"), eval = show_results}
```

#### Community divergence from previous time point

```{r child = here("r_files", "large_community_divergence_from_previous_point.Rmd"), eval = show_results}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_size_classes.Rmd"), eval = show_results}
```

#### Body size distribution {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_body_size_distribution.Rmd"), eval = FALSE}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_median_body_size.Rmd"), eval = show_results}
```

### SL {.tabset .tabset-dropdown}

```{r}
patch_type_input = c("Small connected to large",
                     "Large connected to small")
```

#### Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "SL_biomass.Rmd"), eval = show_results}
```

#### Alpha diversity (Shannon) {.tabset .tabset-pills}

```{r child = here("r_files", "SL_alpha_diversity.Rmd"), eval = show_results}
```

#### Alpha diversity (Species richness) {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_richness.Rmd"), eval = show_results}
```

#### Evenness {.tabset .tabset-pills}

```{r child = here("r_files", "SL_evenness.Rmd"), eval = show_results}
```

#### Species densities {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_densities.Rmd"), eval = show_results}
```

#### Species dominance {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_dominance.Rmd"), eval = show_results}
```

#### Species composition {.tabset .tabset-pills}

```{r child = here("r_files", "SL_species_composition.Rmd"), eval = show_results}
```

#### Community divergence from isolated

```{r child = here("r_files", "SL_community_divergence_from_isolated.Rmd"), eval = show_results}
```

#### Community divergence from previous time point

```{r child = here("r_files", "SL_community_divergence_from_previous_point.Rmd"), eval = show_results}
```

#### Size classes densities {.tabset .tabset-pills}

```{r child = here("r_files", "SL_size_classes.Rmd"), eval = show_results}
```

#### Median body size {.tabset .tabset-pills}

```{r child = here("r_files", "SL_median_body_size.Rmd"), eval = show_results}
```

## Productivity drivers {.tabset .tabset-pills}

```{r child = here("r_files", "relationship_productivity_richness.Rmd"), eval = show_results}
```

```{r child = here("r_files", "relationship_productivity_shannon.Rmd"), eval = show_results}
```

```{r child = here("r_files", "relationship_productivity_evenness.Rmd"), eval = show_results}
```

```{r child = here("r_files", "relationship_productivity_dominance.Rmd"), eval = show_results}
```

## Evaporation {.tabset .tabset-dropdown}

```{r child = here("r_files", "evaporation.Rmd"), eval = FALSE}
```

```{r child = here("r_files", "evaporation_tests.Rmd"), eval = show_results}
```

## Analysis scripts {.tabset .tabset-pills}

### Video analysis

```{r child = here("r_files", "video_analysis_script.Rmd"), class.source = "fold-show"}
```

### Species identification 

```{r child = here("r_files", "species_id_script.Rmd"), class.source = "fold-show"}
```

## Paper

```{r child = here("r_files", "paper.Rmd"), eval = show_results}
```

## Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time
```

## Other

In the .bib file get rid of:

-   book_section

-   computer_program

-   web_page

Check that disturbance_input is what you set:

```{r}
print(paste0("Disturbance = ", disturbance_input))
```

## Bibliography

```{r echo=FALSE, message=FALSE}
save.image(file = "my_environment.RData")
```

```{r}
beep("fanfare")
```