---
title: "main_abundance"
author: "Emanuele Giacomuzzo"
date: "2022-09-08"
output: html_document
---

## Abundance {.tabset .tabset-pills}

### Aim

Here I study how **community** **abundance** changes across patches in the PatchSizePilot. In particular, how does community abundance change according to the size to which the patch is connected? *(Does a small patch connected to a small patch have the same community abundance than a small patch connected to a large patch? And does a large patch connected to a large patch have the same community abundance than a large patch connected to a small patch?)*

### All patches {.tabset .tabset-pills}

```{r child = here("r_files", "abundance", "sections", "patches_all.Rmd")}
source(here("r_files", "abundance", "extracted_sections", "patches_all.R"))
```

### Small patches {.tabset .tabset-pills}

How does community abundance change according to the size to which the patch is connected? *(Does a small patch connected to a small patch have the same community abundance than a small patch connected to a large patch?)*

```{r child = here("r_files", "abundance", "sections", "small_patches.Rmd")}
source(here("r_files", "abundance", "extracted_sections", "small_patches.R"))
```

### Large patches {.tabset .tabset-pills}

How does community abundance change according to the size to which the patch is connected? *(Does a large patch connected to a large patch have the same community abundance than a large patch connected to a small patch?)*

```{r child = here("r_files", "abundance", "sections", "large_patches.Rmd")}
source(here("r_files", "abundance", "extracted_sections", "large_patches.R"))
```

### Isolated patches

How does community abundance change according to the size of isolated patches? *(How does the biomass of small, medium, and large patches change?)*

```{r child = here("r_files", "abundance", "sections", "isolated_patches.Rmd")}
source(here("r_files", "abundance", "extracted_sections", "isolated_patches.R"))
```
