---
title: "regional_biomass_model"
author: "Emanuele Giacomuzzo"
date: '2022-07-22'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r child = "model_t3-t7_time_fitted.Rmd", echo = TRUE, eval = TRUE}
```

## Regional biomass - t3 (strongest time point)

I can't include system_nr as random variable as I have only one data point per system_nr.

```{r dropping-time-points-3}

ds_regional_predicted_shrunk_type_day_12 = ds_regional_predicted_shrunk_type %>%
  filter(day == 12)

#Fixed effect model with fitted time 
fixed_fitted = lm(regional_mean_bioarea ~ 
                          metaecosystem_type  + 
                          disturbance +
                          metaecosystem_type * disturbance,
                        data = ds_regional_predicted_shrunk_type_day_12)

fixed_fitted_2 = lm(regional_mean_bioarea ~ 
                          metaecosystem_type  + 
                          disturbance,
                        data = ds_regional_predicted_shrunk_type_day_12)
anova(fixed_fitted, fixed_fitted_2)
```

Let's get rid of the interaction.

```{r}

summary(fixed_fitted_2)

fixed_fitted_2_no_metaecosystem_type = lm(regional_mean_bioarea ~ 
                          disturbance,
                        data = ds_regional_predicted_shrunk_type_day_12)
summary(fixed_fitted_2_no_metaecosystem_type)
```

**R squared (adjusted)**

Fixed_fittted_2: 0.75

fixed_fitted_2\_no_metaecosystem_type: 0.23

Great! So, if we just keep this data point, the effect size of meta-ecosystem type would be 0.52.

Model diagnostics:

```{r}

par(mfrow=c(2,3))
plot(fixed_fitted_2, which = 1:5)
plot(fixed_fitted_2_no_metaecosystem_type, which = 1:5)
par(mfrow=c(1,1))
```

Okay, next thing to do, I think, is to 