---
title: "Biomass analysis (PatchSizePilot)"
author: "Emanuele Giacomuzzo"
date: '2022-07-07'
output: html_document
editor_options: 
  chunk_output_type: console
bibliography: /Applications/Mendeley/library.bib
---

### Aim

Here I study how **biomass density** changes across treatments in the PatchSizePilot. In particular, I'm studying how biomass density changes across:

-   ecosystems of different size (this is the case in nature, but we need to make sure that it's the case also in our experiment)\
-   ecosystems that are connected (through the flow of nutrients) to an ecosystem of the same size or to an ecosystem that is larger\
-   meta-ecosystems in which patch size is the same or in which one patch has most of the area (we keep the total area of the meta-ecosystem constant)

### Data

```{r child = here("r_files", "biomass", "sections", "data_manipulation.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "data_manipulation.R"))
```

### Regional biomass {.tabset .tabset-dropdown}

#### Medium-Medium vs Small-Large {.tabset .tabset-pills}

We want to understand if the regional biomass produced by an ecosystem with a small and a large patch (`metaecosystem_type = S_L`) is lower than the regional biomass produced by an ecosystem with two medium patches (`metaecosystem_type = M_M`).

##### Plots

Let's start by plotting the single ecosystems to see that everything is fine. To make the patterns clear let's plot the low disturbance and high disturbance in two different figures. We first plot the single meta-ecosystems and then their box plots.

```{r child = here("r_files", "biomass", "sections", "MM_SL_plots.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "MM_SL_plots.R"))
```

We can see that the regional biomass was higher for meta-ecosystems with the same size, regardless of disturbance. As both disturbance levels showed the same pattern, I would just keep the one with low disturbance in the publication, as it shows a stronger pattern.

##### Model time series {.tabset .tabset-pills}

```{r child = here("r_files", "biomass", "sections", "MM_SL_time_series.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "MM_SL_time_series.R"))
```

##### Model single points

```{r MM_SL_time_fitted, child = here("r_files", "biomass", "sections", "MM_SL_single_points.Rmd"), echo = TRUE, eval = TRUE}
source(here("r_files", "biomass", "extracted_sections", "MM_SL_single_points.R"))
```

#### Small-Large vs Small-Large from isolated {.tabset .tabset-pills}

Here I test whether the bioarea of small-large we see is due to meta-ecosystem dynamics or simply to their area.

```{r child = here("r_files", "biomass", "sections", "SL_SL_from_isolated.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "SL_SL_from_isolated.R"))
```

#### Meta-ecosystems of different total size

```{r child = here("r_files", "biomass", "sections", "metaecos_of_different_size.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "metaecos_of_different_size.R"))
```

### Local biomass {.tabset .tabset-dropdown}

#### Small patches {.tabset .tabset-pills}

```{r child = here("r_files", "biomass", "sections", "small_patches.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "small_patches.R"))
```

#### Large patches {.tabset .tabset-pills}

```{r child = here("r_files", "biomass", "sections", "large_patches.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "large_patches.R"))
```

#### Isolated patches

```{r child = here("r_files", "biomass", "sections", "isolated_patches.Rmd")}
source(here("r_files", "biomass", "extracted_sections", "isolated_patches.R"))
```

### Evaporation

```{r child = here("r_files", "biomass", "sections", "evaporation.Rmd"), eval= TRUE}
source(here("r_files", "biomass", "extracted_sections", "evaporation.R"))
```
