---
title: "Biomass analysis (PatchSizePilot)"
author: "Emanuele Giacomuzzo"
date: '2022-07-07'
output: html_document
editor_options: 
  chunk_output_type: console
bibliography: /Applications/Mendeley/library.bib
---

# PatchSizePilot {.tabset}

## Aim

Here I study how **biomass density** changes across treatments in the PatchSizePilot. In particular, I'm studying how biomass density changes across:

-   ecosystems of different size (this is the case in nature, but we need to make sure that it's the case also in our experiment)\
-   ecosystems that are connected (through the flow of nutrients) to an ecosystem of the same size or to an ecosystem that is larger\
-   meta-ecosystems in which patch size is the same or in which one patch has most of the area (we keep the total area of the meta-ecosystem constant)

```{r set-up-environment, echo = FALSE, results = FALSE, message = FALSE}
rm( list = ls(  ) )
cat( "\014" )

start_time = Sys.time()

library("tidyverse")
library("grid")
library("gridExtra") 
library("lme4")
library("here")
library("MuMIn")
library("equatiomatic")
library("knitr")
library("optimx")
library("GenSA")
library("purrr")

knitr::opts_chunk$set(message = FALSE)

source(here("r_files", "biomass", "functions", "biomass_plots.R"))

p = NULL #To run the plotting function
```

## Data manipulation

### Import

```{r import, message = FALSE, echo = TRUE}
culture_info = read.csv(here("data", "PatchSizePilot_culture_info.csv"), header = TRUE)
load(here("data", "population", "t0.RData")); t0 = pop_output
load(here("data", "population", "t1.RData")); t1 = pop_output
load(here("data", "population", "t2.RData")); t2 = pop_output
load(here("data", "population", "t3.RData")); t3 = pop_output
load(here("data", "population", "t4.RData")); t4 = pop_output
load(here("data", "population", "t5.RData")); t5 = pop_output
load(here("data", "population", "t6.RData")); t6 = pop_output
load(here("data", "population", "t7.RData")); t7 = pop_output
rm(pop_output)
```

### Tidy

```{r}
t0$time = NA
t1$time = NA

t0$replicate_video = 1:12 #In t1 I took 12 videos of a single 
t1$replicate_video = 1 #In t1 I took only 1 video/culture
t2$replicate_video = 1 #In t2 I took only 1 video/culture
t3$replicate_video = 1 #In t3 I took only 1 video/culture
t4$replicate_video = 1 #In t4 I took only 1 video/culture
t5$replicate_video = 1 #In t5 I took only 1 video/culture

t6 = t6 %>%
  rename(replicate_video = replicate)
t7 = t7 %>%
  rename(replicate_video = replicate)

#Create an elongated version of t0 so that each of the 110 cultures can have 12 video replicates at t0.
elongating_t0 = NULL
for (video in 1:nrow(t0)){
  for (ID in 1:nrow(culture_info)) {
    elongating_t0 = rbind(elongating_t0, t0[video,])
  }
}

ID_vector = rep(1:nrow(culture_info), 
                times = nrow(t0))

elongating_t0$culture_ID = ID_vector

t0 = merge(culture_info,elongating_t0, by="culture_ID")
t1 = merge(culture_info,t1, by = "culture_ID")
t2 = merge(culture_info,t2, by = "culture_ID")
t3 = merge(culture_info,t3, by = "culture_ID")
t4 = merge(culture_info,t4, by = "culture_ID")
t5 = merge(culture_info,t5, by = "culture_ID")
t6 = merge(culture_info,t6, by = "culture_ID")
t7 = merge(culture_info,t7, by = "culture_ID")
ds = rbind(t0, t1, t2, t3, t4, t5, t6, t7)
rm(elongating_t0, t0, t1, t2, t3, t4, t5, t6, t7)

ds$time_point[ds$time_point=="t0"] = 0
ds$time_point[ds$time_point=="t1"] = 1
ds$time_point[ds$time_point=="t2"] = 2
ds$time_point[ds$time_point=="t3"] = 3
ds$time_point[ds$time_point=="t4"] = 4
ds$time_point[ds$time_point=="t5"] = 5
ds$time_point[ds$time_point=="t6"] = 6
ds$time_point[ds$time_point=="t7"] = 7
ds$time_point = as.character(ds$time_point)

ds$day = NA
ds$day[ds$time_point== 0] = 0
ds$day[ds$time_point== 1] = 4
ds$day[ds$time_point== 2] = 8
ds$day[ds$time_point== 3] = 12
ds$day[ds$time_point== 4] = 16
ds$day[ds$time_point== 5] = 20
ds$day[ds$time_point== 6] = 24
ds$day[ds$time_point== 7] = 28

ds = ds %>% 
  select(culture_ID, 
         patch_size, 
         disturbance, 
         metaecosystem_type, 
         bioarea_per_volume, 
         replicate_video, 
         time_point,
         day,
         metaecosystem, 
         system_nr, 
         eco_metaeco_type)

ds = ds[, c("culture_ID", 
            "system_nr", 
            "disturbance", 
            "time_point",
            "day", 
            "patch_size", 
            "metaecosystem", 
            "metaecosystem_type", 
            "eco_metaeco_type", 
            "replicate_video",
            "bioarea_per_volume")]

ds$eco_metaeco_type = factor(ds$eco_metaeco_type, 
                             levels = c('S', 
                                        'S (S_S)', 
                                        'S (S_L)', 
                                        'M', 
                                        'M (M_M)', 
                                        'L', 
                                        'L (L_L)', 
                                        'L (S_L)'))

#ds$patch_size = factor(ds$patch_size,
#                        levels = c ('S', 'M', 'L'))

#ds$metaecosystem_type = factor(ds$metaecosystem_type, 
#levels = c ('S_S', 'M_M', 'L_L', 'S_L'))

ecosystems_to_take_off = 60 #Culture number 60 because it was spilled
ds = ds %>%
  filter(! culture_ID %in% ecosystems_to_take_off)
```

### Create regional data set

```{r regional-biomass}
ds_regional = ds %>%
  filter(metaecosystem == "yes") %>%
  group_by(culture_ID, 
           system_nr, 
           disturbance, 
           day, 
           time_point, 
           patch_size, 
           metaecosystem_type) %>%
  summarise(patch_mean_bioarea_across_videos = mean(bioarea_per_volume)) %>%
  group_by(system_nr, disturbance, day, time_point, metaecosystem_type) %>%
  summarise(regional_mean_bioarea = mean(patch_mean_bioarea_across_videos))

metaecosystems_to_take_off = 40 #System 40 was the system of culture 60 that I spilled
ds_regional = ds_regional %>%
  filter(! system_nr %in% metaecosystems_to_take_off)
```

```{r child = here("r_files", "biomass", "sections", "plots.Rmd"), eval = FALSE}
#source(here("r_files", "biomass", "extracted_sections", "plots.R"))
```

## Regional biomass {.tabset}

### Aim

We are here going to model 

### M_M vs S_L {.tabset}

We want to understand if the regional biomass produced by an ecosystem with a small and a large patch (metaecosystem_type = S_L) is lower than the regional biomass produced by an ecosystem with two medium patches (metaecosystem_type = M_M).

#### Tidy & plot

First of all, let's modify the data set including the regional biomass of our meta-ecosystems. In this data set, we want to have the regional biomass of the meta-ecosystems (averaged first across videos and then across patches) in which we:

-   Include only the meta-ecosystems in which patches had both medium size (metaecosystem_type = M_M) and meta-ecosystems in which patches had one a small size and the other large size (metaecosystem_type = S_L).

-   Take off the first two point (day 0 and day = 4). This is because the first perturbation happened only at day 5.

```{r}
ds_regional_shrunk_type_n_day = ds_regional %>%
    filter (metaecosystem_type == "M_M" | metaecosystem_type == "S_L", 
            time_point >= 2)
```

Let's start by plotting the single ecosystems to see that everything is fine.

```{r}
ds_regional %>%
    filter ( disturbance == "low") %>%
    filter (metaecosystem_type == "S_L" | metaecosystem_type == "M_M") %>%
    ggplot (aes(x = day,
                y = regional_mean_bioarea,
                group = system_nr,
                fill = system_nr,
                color = system_nr,
                linetype = metaecosystem_type)) +
    geom_point() +
    geom_line () +
    labs(x = "Day", 
         y = "Regional biomass (average bioarea between 2 patches/µl)",
         title = "Disturbance = low") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())

ds_regional %>%
    filter ( disturbance == "high") %>%
    filter (metaecosystem_type == "S_L" | metaecosystem_type == "M_M") %>%
    ggplot (aes(x = day,
                y = regional_mean_bioarea,
                group = system_nr,
                fill = system_nr,
                color = system_nr,
                linetype = metaecosystem_type)) +
    geom_point() +
    geom_line () +
    labs(x = "Day", 
         y = "Regional biomass (average bioarea between 2 patches/µl)",
         title = "Disturbance = high") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())
```

Let's then plot their mean and standard deviation.

```{r}
final_plot = ds_regional %>%
  group_by(metaecosystem_type, disturbance, day) %>%
  summarise(mean_bioarea = mean(regional_mean_bioarea), 
            sd_bioarea = sd(regional_mean_bioarea)) %>%
  filter(disturbance == "low") %>%
  filter (metaecosystem_type == "S_L" | metaecosystem_type == "M_M") %>%
  ggplot (aes(x = day,
                y = mean_bioarea,
                fill = metaecosystem_type,
                color = metaecosystem_type)) +
  #geom_point(stat = "summary", fun = "mean") +
  geom_line (stat = "summary", 
             fun = "mean", 
             position=position_dodge(width=0.5)) +
  geom_pointrange(
    aes(ymin = mean_bioarea - sd_bioarea, 
        ymax = mean_bioarea + sd_bioarea),
    position=position_dodge(width=0.5)) +
  labs(x = "Day", 
       y = "Regional biomass (average bioarea between 2 patches/µl)",
       title = "Disturbance = low",
       color='', 
       fill='') +
  scale_fill_discrete(labels = c("Meta-ecosystem with patches of same size", 
                                 "Meta-ecosystem with patches of different size")) +
  scale_color_discrete(labels = c("Meta-ecosystem with patches of same size", 
                                  "Meta-ecosystem with patches of different size")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
final_plot

ds_regional %>%
  group_by(metaecosystem_type, disturbance, day) %>%
  summarise(mean_bioarea = mean(regional_mean_bioarea), 
            sd_bioarea = sd(regional_mean_bioarea)) %>%
  filter(disturbance == "high") %>%
  filter (metaecosystem_type == "S_L" | metaecosystem_type == "M_M") %>%
  ggplot (aes(x = day,
                y = mean_bioarea,
                fill = metaecosystem_type,
                color = metaecosystem_type)) +
  #geom_point(stat = "summary", fun = "mean") +
  geom_line (stat = "summary", 
             fun = "mean", 
             position=position_dodge(width=0.5)) +
  geom_pointrange(
    aes(ymin = mean_bioarea - sd_bioarea, 
        ymax = mean_bioarea + sd_bioarea),
    position=position_dodge(width=0.5)) +
  labs(x = "Day", 
       y = "Regional biomass (average bioarea between 2 patches/µl)",
       title = "Disturbance = high",
       color='', 
       fill='') +
  scale_fill_discrete(labels = c("Meta-ecosystem with patches of same size", 
                                 "Meta-ecosystem with patches of different size")) +
  scale_color_discrete(labels = c("Meta-ecosystem with patches of same size", 
                                  "Meta-ecosystem with patches of different size")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())
```

We can see that the regional biomass was higher for meta-ecosystems with the same size, regardless of the . As both disturbance levels showed the same pattern, I would just keep the one with low disturbance in the publication, as it shows a stronger pattern.

```{r, fig.align='center', fig.cap = "Figure 2 of the paper: Regional biomass production in meta-ecosystems of the same total area, but whose two patches are either identical (red, medium-medium meta-ecosystem) or one is five times larger (blue, small-large meta-ecosystem). Error bars represent the standard deviation and point represents the mean at a specific time point. For clarity, only the low disturbance treatment is shown here. See the Appendix for equivalent the figure of the high disturbance treatment."}
final_plot
```

#### Time as random effect

```{r child = here("r_files", "biomass", "sections", "M_M-S_L_time_random.Rmd"), echo = TRUE, eval = TRUE}
#source(here("r_files", "biomass", "extracted_sections", "M_M-S_L_time_random.R"))
```

#### Time as explanatory variable

```{r child = here("r_files", "biomass", "sections", "M_M-S_L_time_fitted.Rmd"), echo = TRUE, eval = TRUE}
#source(here("r_files", "biomass", "extracted_sections", "M_M-S_L_time_fitted.R"))
```

## Local biomass {.tabset}

### Aim

Here we are going to model how local biomass changes across treatments. At the end of the day, however, we are interested in knowing the difference between the biomass of:
- an isolated small patch (S)
- a small patch connected to another small patch S (S_S)
- a small patch connected to a larger patch S (S_L)

```{r}

ds %>%
    filter (  eco_metaeco_type == "S" | 
              eco_metaeco_type == "S (S_S)" |
              eco_metaeco_type == "S (S_L)") %>%
    ggplot(aes(x = day,
               y = bioarea_per_volume,
               fill = eco_metaeco_type,
               color = eco_metaeco_type)) +
    geom_point(stat = "summary", fun = "mean") +
    geom_line(stat = "summary", fun = "mean") +
    labs(x = "Day", 
         y = "Local biomass (bioarea/µl)", 
         color = '', 
         fill = '') +
    scale_fill_discrete(labels = c("Isolated patch", 
                                   "Patch connected to patch of the same size", 
                                   "Patch connected to larger patch")) +
    scale_color_discrete(labels = c("Isolated patch", 
                                    "Patch connected to patch of the same size", 
                                    "Patch connected to larger patch")) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())
```

*Figure 3. Local biomass production in patches that are either isolated (red, small isolated patches), connected to patches of the same size (green, patches of small-small meta-ecosystems), or connected to patches five times larger (blue, small patches of small-large meta-ecosystems).*

```{r child = here("r_files", "biomass", "sections", "S-S_S_and_S-S_L.Rmd")}
#source(here("r_files", "biomass", "extracted_sections", "S-S_S_and_S-S_L.R"))
```

```{r child = here("r_files", "biomass", "sections", "S_and_S-S_L.Rmd")}
#source(here("r_files", "biomass", "extracted_sections", "S_and_S-S_L.R"))
```

Problem of rescaling variables

```{r child = here("r_files", "biomass", "sections", "S_and_S-S_S.Rmd")}
#source(here("r_files", "biomass", "extracted_sections", "S_and_S-S_S.R"))
```

```{r child = here("r_files", "biomass", "sections", "L_and_L-L_L.Rmd")}
#source(here("r_files", "biomass", "extracted_sections", "L_and_L-L_L.R"))
```

```{r child = here("r_files", "biomass", "sections", "L_and_L-S_L.Rmd")}
#source(here("r_files", "biomass", "extracted_sections", "L_and_L-S_L.R"))
```

## Modelling considerations

Before start modelling, just a few considerations on mixed effect models and model selection.

### Mixed effects models

-   To build the mixed effect models we will use the R package lme4. See page 6 of [this PDF](https://cran.r-project.org/web/packages/lme4/vignettes/lmer.pdf) to know more about the syntaxis of this package.

-   To do model diagnostics of mixed effect models, I'm going to look at the following two plots (as suggested by @Zuur2009, page 487):

    -   Quantile-quantile plots

    -   Partial residual plots

-   The effect size of the explaining variables is calculated in the mixed effect models as marginal and conditional r squared. The marginal r squared is how much variance is explained by the fixed effects. The conditional r squared is how much variance is explained by the fixed and the random effects. The marginal and conditional r squared are calculated using the package `MuMIn`. The computation is based on the methods of @Nakagawa2017. For the coding and interpretation of these r squared check the [documentation for the r.squaredGLMM function](https://rdrr.io/cran/MuMIn/man/r.squaredGLMM.html)

### Model selection

-   I am starting from the largest model and then simplifying because ... (see statistical modelling course at ETH).

-   I am going to select the best model according to BIC instead of AIC. This is because BIC is better for understanding and AIC for predicting. @Halsey2019 also suggests this approach instead of p values.

## Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time #For some reason it doesn't work 
```

## Bibliography

```{r extract-sections, include = FALSE, eval = FALSE}

#You can just run this to run all the sections so then you can work on them. 
sections.path = here("r_files", "biomass")
r.files = list.files(sections.path)
rmd.files = r.files[grepl(".Rmd", r.files)]
extracted.path = here("r_files", "biomass", "extracted_sections")

purrr::map(rmd.files, function(file.i) {
  
  file.name = gsub(".Rmd", "", file.i)
  extracted.file <- paste0(file.name, ".R")
  knitr::purl(
    file.path(sections.path, file.i),
    file.path(extracted.path, extracted.file)
    )
  
})
```
