---
title: "Biomass analysis (PatchSizePilot)"
author: "Emanuele Giacomuzzo"
date: '2022-07-07'
output:
  html_document:
    toc: true
    theme: united
editor_options: 
  chunk_output_type: console
bibliography: /Applications/Mendeley/library.bib
---

Here I study how **biomass density** changes across treatments in the PatchSizePilot. In particular, I'm studying how biomass density changes across:

-   ecosystems of different size (this is the case in nature, but we need to make sure that it's the case also in our experiment)\
-   ecosystems that are connected (through the flow of nutrients) to an ecosystem of the same size or to an ecosystem that is larger\
-   meta-ecosystems in which patch size is the same or in which one patch has most of the area (we keep the total area of the meta-ecosystem constant)

```{r set-up-environment, echo = FALSE, results = FALSE, message = FALSE}
start_time = Sys.time()

rm( list = ls(  ) )
cat( "\014" )
library("tidyverse")
library("grid")
library("gridExtra") 
library("lme4")
library("here")
library("MuMIn")
library("equatiomatic")
library("knitr")
library("optimx")
library("GenSA")

knitr::opts_chunk$set(message = FALSE)

source(here("r_files", "biomass", "functions", "biomass_plots.R"))

p = NULL #To run the plotting function
```

# Import

```{r import, message = FALSE, echo = TRUE}
culture_info = read.csv(here("data", "PatchSizePilot_culture_info.csv"), header = TRUE)
load(here("data", "population", "t0.RData")); t0 = pop_output
load(here("data", "population", "t1.RData")); t1 = pop_output
load(here("data", "population", "t2.RData")); t2 = pop_output
load(here("data", "population", "t3.RData")); t3 = pop_output
load(here("data", "population", "t4.RData")); t4 = pop_output
load(here("data", "population", "t5.RData")); t5 = pop_output
load(here("data", "population", "t6.RData")); t6 = pop_output
load(here("data", "population", "t7.RData")); t7 = pop_output
rm(pop_output)
```

# Tidy

```{r tidy-up}
t0$time = NA
t1$time = NA

t0$replicate_video = 1:12 #In t1 I took 12 videos of a single 
t1$replicate_video = 1 #In t1 I took only 1 video/culture
t2$replicate_video = 1 #In t2 I took only 1 video/culture
t3$replicate_video = 1 #In t3 I took only 1 video/culture
t4$replicate_video = 1 #In t4 I took only 1 video/culture
t5$replicate_video = 1 #In t5 I took only 1 video/culture

t6 = t6 %>%
  rename(replicate_video = replicate)
t7 = t7 %>%
  rename(replicate_video = replicate)

#Create an elongated version of t0 so that each of the 110 cultures can have 12 video replicates at t0.
elongating_t0 = NULL
for (video in 1:nrow(t0)){
  for (ID in 1:nrow(culture_info)) {
    elongating_t0 = rbind(elongating_t0, t0[video,])
  }
}

ID_vector = rep(1:nrow(culture_info), 
                times = nrow(t0))

elongating_t0$culture_ID = ID_vector

t0 = merge(culture_info,elongating_t0, by="culture_ID")
t1 = merge(culture_info,t1, by = "culture_ID")
t2 = merge(culture_info,t2, by = "culture_ID")
t3 = merge(culture_info,t3, by = "culture_ID")
t4 = merge(culture_info,t4, by = "culture_ID")
t5 = merge(culture_info,t5, by = "culture_ID")
t6 = merge(culture_info,t6, by = "culture_ID")
t7 = merge(culture_info,t7, by = "culture_ID")
ds = rbind(t0, t1, t2, t3, t4, t5, t6, t7)
rm(elongating_t0, t0, t1, t2, t3, t4, t5, t6, t7)

ds$time_point[ds$time_point=="t0"] = 0
ds$time_point[ds$time_point=="t1"] = 1
ds$time_point[ds$time_point=="t2"] = 2
ds$time_point[ds$time_point=="t3"] = 3
ds$time_point[ds$time_point=="t4"] = 4
ds$time_point[ds$time_point=="t5"] = 5
ds$time_point[ds$time_point=="t6"] = 6
ds$time_point[ds$time_point=="t7"] = 7
ds$time_point = as.character(ds$time_point)

ds$day = NA
ds$day[ds$time_point== 0] = 0
ds$day[ds$time_point== 1] = 4
ds$day[ds$time_point== 2] = 8
ds$day[ds$time_point== 3] = 12
ds$day[ds$time_point== 4] = 16
ds$day[ds$time_point== 5] = 20
ds$day[ds$time_point== 6] = 24
ds$day[ds$time_point== 7] = 28

ds = ds %>% 
  select(culture_ID, 
         patch_size, 
         disturbance, 
         metaecosystem_type, 
         bioarea_per_volume, 
         replicate_video, 
         time_point,
         day,
         metaecosystem, 
         system_nr, 
         eco_metaeco_type)

ds = ds[, c("culture_ID", 
            "system_nr", 
            "disturbance", 
            "time_point",
            "day", 
            "patch_size", 
            "metaecosystem", 
            "metaecosystem_type", 
            "eco_metaeco_type", 
            "replicate_video",
            "bioarea_per_volume")]

ds$eco_metaeco_type = factor(ds$eco_metaeco_type, 
                             levels=c('S', 
                                      'S (S_S)', 
                                      'S (S_L)', 
                                      'M', 
                                      'M (M_M)', 
                                      'L', 
                                      'L (L_L)', 
                                      'L (S_L)'))

ecosystems_to_take_off = 60 #Culture number 60 because it was spilled
ds = ds %>%
  filter(! culture_ID %in% ecosystems_to_take_off)
```

# Create regional data set

```{r regional-biomass}
ds_regional = ds %>%
  filter(metaecosystem == "yes") %>%
  group_by(culture_ID, system_nr, disturbance, day, time_point, patch_size, metaecosystem_type) %>%
  summarise(patch_mean_bioarea_across_videos = mean(bioarea_per_volume)) %>%
  group_by(system_nr, disturbance, day, time_point, metaecosystem_type) %>%
  summarise(regional_mean_bioarea = mean(patch_mean_bioarea_across_videos))

metaecosystems_to_take_off = 40 #System 40 was the system of culture 60 that I spilled
ds_regional = ds_regional %>%
  filter(! system_nr %in% metaecosystems_to_take_off)
```

```{r child = "plots.Rmd", eval = FALSE}
```

# Modelling considerations

Before start modelling, just a few considerations on mixed effect models and model selection.

## Mixed effects models

-   To build the mixed effect models we will use the R package lme4. See page 6 of [this PDF](https://cran.r-project.org/web/packages/lme4/vignettes/lmer.pdf) to know more about the syntaxis of this package.

-   To do model diagnostics of mixed effect models, I'm going to look at the following two plots (as suggested by @Zuur2009, page 487):

    -   Quantile-quantile plots

    -   Partial residual plots

-   The effect size of the explaining variables is calculated in the mixed effect models as marginal and conditional r squared. The marginal r squared is how much variance is explained by the fixed effects. The conditional r squared is how much variance is explained by the fixed and the random effects. The marginal and conditional r squared are calculated using the package `MuMIn`. The computation is based on the methods of @Nakagawa2017. For the coding and interpretation of these r squared check the [documentation for the r.squaredGLMM function](https://rdrr.io/cran/MuMIn/man/r.squaredGLMM.html)

## Model selection 

-   I am starting from the largest model and then simplifying because ... (see statistical modelling course at ETH).

-   I am going to select the best model according to BIC instead of AIC. This is because BIC is better for understanding and AIC for predicting.

# Regional biomass modelling

When modelling the regional biomass, we want to understand if the regional biomass produced by an ecosystem with a small and a large patch (metaecosystem_type = S_L) is lower than the regional biomass produced by an ecosystem with two medium patches (metaecosystem_type = M_M).

## Tidy

First of all, let's modify the data set including the regional biomass of our meta-ecosystems. In this data set, we want to have the regional biomass of the meta-ecosystems (averaged first across videos and then across patches) in which we:

-   Include only the meta-ecosystems in which patches had both medium size (metaecosystem_type = M_M) and meta-ecosystems in which patches had one a small size and the other large size (metaecosystem_type = S_L).

-   Take off the first two point (day 0 and day = 4). This is because the first perturbation happened only at day 5.

```{r}
ds_regional_shrunk_type_n_day = ds_regional %>%
    filter (metaecosystem_type == "M_M" | metaecosystem_type == "S_L", 
            time_point >= 2)
```

## Plot

```{r}
ds_regional %>%
    filter (metaecosystem_type == "S_L" | metaecosystem_type == "M_M") %>%
    ggplot (aes(x = day,
                y = regional_mean_bioarea,
                fill = metaecosystem_type,
                color = metaecosystem_type)) +
    geom_point(stat = "summary", fun = "mean") +
    geom_line (stat = "summary", fun = "mean") +
    labs(x = "Day", 
         y = "Regional biomass (average bioarea between 2 patches/µl)", 
         color='Meta-ecosystem type', 
         fill='Meta-ecosystem type') +
    scale_fill_discrete(labels = c("Patches of same size", "Patches of different size")) +
    scale_color_discrete(labels = c("Patches of same size", "Patches of different size")) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())
```

```{r child = "no_time_fitting_t2-t7.Rmd", echo = TRUE, eval = TRUE}
```

```{r child = "time_fitting.Rmd", echo = TRUE, eval = TRUE}
```

```{r child = "time_fitted_t2-t7.Rmd", echo = TRUE, eval = TRUE}
```

```{r child = "time_fitted_each_time_point.Rmd", echo = TRUE, eval = TRUE}
```

```{r child = "time_fitted_different_time_periods.Rmd", echo = TRUE, eval = TRUE}
```

# Local biomass modelling

## Tidy

```{r}

ds_local_S = ds %>%
  filter (eco_metaeco_type == "S" | eco_metaeco_type == "S (S_S)" | eco_metaeco_type == "S (S_L)") %>%
  filter(time_point >= 2) #Let's take off the first two time points which are before the first disturbance event.
```

## Plot

```{r}

ds_local_S %>%
    filter (eco_metaeco_type == "S" | eco_metaeco_type == "S (S_S)" | eco_metaeco_type == "S (S_L)") %>%
    ggplot(aes(x = day,
               y = bioarea_per_volume,
               fill = eco_metaeco_type,
               color = eco_metaeco_type)) +
    geom_point(stat = "summary", fun = "mean") +
    geom_line(stat = "summary", fun = "mean") +
    labs(x = "Day", y = "Local biomass (bioarea/µl)", color='Patch type', fill='Patch type') +
    #scale_fill_discrete(labels = c("Connected to same sized patch", "Connected to larger patch")) +
    #scale_color_discrete(labels = c("Connected to same sized patch", "Connected to larger patch")) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

## Model selection

```{r}

full_model_uncorrelated = lmer(bioarea_per_volume ~ 
                    metaecosystem_type  + 
                    disturbance + 
                    metaecosystem_type * disturbance + 
                    (metaecosystem_type || day) + 
                    (disturbance || day) + 
                    (metaecosystem_type*disturbance  || day) + 
                    (metaecosystem_type || system_nr) + 
                    (disturbance || system_nr) + 
                    (metaecosystem_type*disturbance  || system_nr), 
                  data = ds_local_S, 
                  REML = FALSE)

full_model_correlated = lmer(bioarea_per_volume ~ 
                               metaecosystem_type  + 
                               disturbance + 
                               metaecosystem_type * disturbance + 
                               (metaecosystem_type | day) + 
                               (disturbance | day) + 
                               (metaecosystem_type*disturbance  | day) + 
                               (metaecosystem_type | system_nr) + 
                               (disturbance | system_nr) + 
                               (metaecosystem_type*disturbance  | system_nr), 
                             data = ds_local_S, 
                             REML = FALSE)

anova(full_model_uncorrelated, full_model_correlated)

no_system_nr_model = lmer(bioarea_per_volume ~ 
                            metaecosystem_type  + 
                            disturbance + 
                            metaecosystem_type * disturbance + 
                            (metaecosystem_type || day) + 
                            (disturbance || day) + 
                            (metaecosystem_type*disturbance || day), 
                          data = ds_local_S, 
                          REML = FALSE)

anova(full_model_uncorrelated, no_system_nr_model)

fixed_effects_model = lm(bioarea_per_volume ~ 
                           metaecosystem_type  + 
                           disturbance +
                           metaecosystem_type * disturbance, 
                         data = ds_local_S)

anova(no_system_nr_model, fixed_effects_model)

no_interaction_model = lmer(bioarea_per_volume ~ 
                              metaecosystem_type + 
                              disturbance  + 
                              (metaecosystem_type || day) + 
                              (disturbance || day), 
                            data = ds_local_S, 
                            REML = FALSE)

anova(no_system_nr_model, no_interaction_model)

no_slopes_model = lmer(bioarea_per_volume ~ 
                         metaecosystem_type + 
                         disturbance  + 
                         (1 | day), 
                       data = ds_local_S, 
                       REML = FALSE)

anova(no_interaction_model, no_slopes_model)
#the two models are highly different. AIC suggests using no_interaction_model. BIC suggests using no_slopes_model. I'll then keep the no_slopes_model.

best_model = no_slopes_model
```

## Analysis of the best model

```{r}

model.null = lm(bioarea_per_volume ~ 
                  1, 
                  data = ds_local_S)

r2_best = r.squaredGLMM(best_model)
r2_best = round(r2_best, digits = 3)

anova = anova(best_model, model.null)
p_best = anova$`Pr(>Chisq)`[2]
p_best = round(p_best, digits = 5)

if (p_best < 0.00001) {
  p_best = "< 0.00001"
}
```

# Running time

```{r running-time, echo = FALSE, eval = FALSE}
end_time = Sys.time()
print(end_time - start_time) #For some reason it doesn't work 
```

# Bibliography
