---
html_document:
  toc: yes
  toc_float: yes
  code_folding: hide
  number_sections: yes
  includes:
    after_body: "tabset-dropdown.html"
author: "Emanuele Giacomuzzo"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output:
  html_document:
    code_folding: hide
    profiling: yes
title: "PatchSize"
editor_options:
  chunk_output_type: console
---

```{r child = here::here("2_r_files", "1_set_packages.Rmd"), echo = FALSE, message = FALSE, cache = FALSE, autodep = FALSE}
```

```{r child = here("2_r_files", "2_set_functions.Rmd"), echo=FALSE}
```

#  {.tabset}

## Design {.tabset .tabset-pills}

```{r child = here("2_r_files", "3_design.Rmd")}
```

## Parameters

```{r child = here("2_r_files", "4_set_parameters.Rmd"), class.source = 'fold-show'}
```

## Data {.tabset .tabset-dropdown}

```{r child = here("2_r_files", "5_ds_ecosystems_info.Rmd")}
```

```{r child = here("2_r_files", "6_ds_individuals.Rmd")}
```

```{r child = here("2_r_files", "7_ds_ecosystems.Rmd")}
```

```{r child = here("2_r_files", "8_ds_ecosystems_effect_size.Rmd")}
```

```{r child = here("2_r_files", "9_ecos_combinations.Rmd")}
```

```{r child = here("2_r_files", "10_ecos_combinations_sets.Rmd")}
```

```{r child = here("2_r_files", "11_ds_metaecos.Rmd")}
```

```{r child = here("2_r_files", "12_ds_classes.Rmd"), eval = FALSE}
```

```{r child = here("2_r_files", "13_ds_classes_effect_size.Rmd"), eval = FALSE}
```

## Meta-ecosystems {.tabset .tabset-pills}

### Alpha {.tabset .tabset-pills}

```{r}
response_variable_selected = "mean_shannon"
```

```{r child = here("2_r_files", "15_metaecos_variable_iterated.Rmd")}
```

### Beta {.tabset .tabset-pills}

```{r}
response_variable_selected = "bray_curtis"
```

```{r child = here("2_r_files", "15_metaecos_variable_iterated.Rmd")}
```

### Gamma {.tabset .tabset-pills}

```{r}
response_variable_selected = "metaecosystem_richness"
```

```{r child = here("2_r_files", "15_metaecos_variable_iterated.Rmd")}
```

### Biomass {.tabset .tabset-pills}

```{r}
response_variable_selected = "total_metaecosystem_bioarea_mm2"
```

```{r child = here("2_r_files", "15_metaecos_variable_iterated.Rmd")}
```

## Ecosystems {.tabset .tabset-pills}

### Shannon {.tabset .tabset-pills}

```{r}
response_variable_selected = "shannon"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### Biomass {.tabset .tabset-pills}

```{r}
response_variable_selected = "sqrt_bioarea_mm2_per_ml"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### Richness {.tabset .tabset-pills}

```{r}
response_variable_selected = "species_richness"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### Evenness {.tabset .tabset-pills}

```{r}
response_variable_selected = "evenness_pielou"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### Median Size {.tabset .tabset-pills}

```{r}
response_variable_selected = "median_body_area_µm2"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### Auto/Hetero {.tabset .tabset-pills}

```{r}
response_variable_selected = "sqrt_auto_hetero_ratio"
```

```{r child = here("2_r_files", "16_ecos_variable.Rmd")}
```

### BEF {.tabset .tabset-pills}

```{r child = here("2_r_files", "17_ecos_BEF.Rmd")}
```

### Populations

```{r child = here("2_r_files", "18_ecos_populations.Rmd"), eval = FALSE}
```

## Results {.tabset .tabset-pills}

### Meta-ecosystem diversity & function

```{r child = here("2_r_files", "19_metaecos_paper.Rmd"), eval = FALSE}
```

```{r child = here("2_r_files", "20_metaecos_present.Rmd"), echo = FALSE, eval = FALSE}
```

### Ecosystem diversity & function

```{r child = here("2_r_files", "21_S_L_paper.Rmd"), eval = FALSE} 
```

```{r child = here("2_r_files", "22_S_L_present.Rmd"), eval = FALSE} 
```

```{r child = here("2_r_files", "23_M_paper.Rmd"), eval = FALSE} 
```

### Ecosystem autotrophic/heterotrophic ratio

```{r child = here("2_r_files", "24_unconnected_AH_ratio_paper.Rmd"), eval = FALSE}
```

## Evaporation

```{r child = here("2_r_files", "25_test_evaporation.Rmd")}
```

## Analysis scripts {.tabset .tabset-pills}

### Video analysis

```{r child = here("2_r_files", "26_script_BEMOVI_video_analysis.Rmd"), class.source = "fold-show"}
```

### Species identification

```{r child = here("2_r_files", "27_script_BEMOVI_species_id.Rmd"), class.source = "fold-show"}
```

## Other

```{r child = here("2_r_files", "28_show_other.Rmd")}
```