---
title: "Other"
output: html_document
date: "2023-08-21"
editor_options: 
  chunk_output_type: console
---

### Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
round(end_time - start_time, digits = 1)
```

### Useful code

If you want to change a certain part of the code using the following code in Unix:

```{r eval = FALSE, class.source = 'fold-show'}
#Rmd script
cd /Users/Ema/Documents/Github/PatchSize/3_r_files
sed -i '' 's/old_string/new_string/g' *.Rmd

#R script
cd /Users/ema/Documents/GitHub/PatchSize/3_r_files/functions
sed -i '' 's/old_string/new_string/g' *.R
```

you want to share a dataset and get a reproducible object, use the following R code:

```{r eval = FALSE}
dput()
```

### Crashed cultures

The only type of ecosystem where all cultures crashed was small connected to small at high disturbance.

### R version

```{r}
R.version.string
```

### R package versions

The R packages we used with their version are as follows:

```{r}
sessionInfo()
```

#### References

```{r echo=FALSE, message=FALSE}
save.image(file = here("3_results", "environments", "environment_at_the_end_of_analysis.RData"))
```
