---
title: "MM_SL_single_points"
author: "Emanuele Giacomuzzo"
date: "2022-08-05"
output: html_document
editor_options: 
  chunk_output_type: console
---

**Model selection**

I'll do model selection only on time point number 3 (however, I have done it also with time point 4,5,6,7 and they all give me the same result). Let's start from the full model.

*I can't construct it from a mixed model because the following error pops up:*

-   *Error: number of levels of each grouping factor must be \< number of observations (problems: system_nr)*

```{r}
full = lm(regional_mean_bioarea ~
              metaecosystem_type +
              disturbance +
              disturbance : metaecosystem_type,
            data = ds_regional %>%
              filter(time_point == 3) %>%
              filter(metaecosystem_type == "M_M" |
                     metaecosystem_type == "S_L"))
```

*Should we keep D \* M?*

```{r}
no_MD = lm(regional_mean_bioarea ~
              metaecosystem_type +
              disturbance,
            data = ds_regional %>%
              filter(time_point == 3) %>%
              filter(metaecosystem_type == "M_M" |
                     metaecosystem_type == "S_L"))

anova(full, no_MD)
AIC(full, no_MD)
```

No.

**Best model**

Therefore, our best model is

$$
Regional \: Bioarea = M + D
$$
