---
title: "model_all_points_without_time_fitting"
author: "Emanuele Giacomuzzo"
date: '2022-07-22'
output: html_document
editor_options: 
  chunk_output_type: console
---

###### Tidy

First of all, let's modify the data set including the regional biomass of our meta-ecosystems. In this data set, we want to have the regional biomass of the meta-ecosystems (averaged first across videos and then across patches) in which we:

-   Include only the meta-ecosystems in which patches had both medium size (metaecosystem_type = M_M) and meta-ecosystems in which patches had one a small size and the other large size (metaecosystem_type = S_L).

-   Take off the first two point (day 0 and day = 4). This is because the first perturbation happened only at day 5.

```{r}
ds_regional_MM_SL_t2t7 = ds_regional %>%
    filter (metaecosystem_type == "M_M" | metaecosystem_type == "S_L", 
            time_point >= 2)
```

###### Model selection

Let's start from the largest mixed effect model makes sense to construct. This will include:

-   As fixed effect: metaecosystem type (M), disturbance (D), and their interaction (M \* D)
-   As random effect (random intercept and slope): day and the number of the metaecosystem (system_nr).

We are actually going to construct two full models. One with the correlated and one with the uncorrelated random slopes and intercept, the other without

  
  
  
*(1) Should we keep the correlation between intercept and slopes (\|)?*

```{r}
full_model_correlated = lmer(regional_mean_bioarea ~ 
                             metaecosystem_type  + 
                             disturbance + 
                             metaecosystem_type * disturbance + 
                             (metaecosystem_type | day) + 
                             (disturbance | day) + 
                             (metaecosystem_type*disturbance  | day) +
                             (1 | system_nr) , 
                             data = ds_regional_MM_SL_t2t7, 
                             REML = FALSE)

full_model_uncorrelated = lmer(regional_mean_bioarea ~ 
                    metaecosystem_type  + 
                    disturbance + 
                    metaecosystem_type * disturbance + 
                    (metaecosystem_type || day) + 
                    (disturbance || day) + 
                    (metaecosystem_type*disturbance  || day) +
                    (1 | system_nr) ,
                  data = ds_regional_MM_SL_t2t7, 
                  REML = FALSE)

anova(full_model_uncorrelated, full_model_correlated)
```

Yes (according to BIC and AIC). Interestingly enough, the p-value is 1 (how should I interpret this?).

  
  
  
*(2) Should we keep M \** D ?

```{r, message=FALSE}
no_interaction_model = lmer(regional_mean_bioarea ~ 
                              metaecosystem_type + 
                              disturbance  + 
                              (metaecosystem_type | day) + 
                              (disturbance | day) +
                              (1 | system_nr), 
                            data = ds_regional_MM_SL_t2t7, 
                            REML = FALSE)

anova(full_model_correlated, no_interaction_model)
```

No (according to AIC and BIC). The p-value is also here almost 1 (how should I interpret this?).

  
  
  
*(3) Should we keep (M \| day)?*

```{r, message=FALSE}
no_metaeco_slopes_model = lmer(regional_mean_bioarea ~ 
                                 metaecosystem_type + 
                                 disturbance  + 
                                 (disturbance | day) +
                                 (1 | system_nr), 
                               data = ds_regional_MM_SL_t2t7, 
                               REML = FALSE)

anova(no_interaction_model, no_metaeco_slopes_model)
```

Yes (according to AIC and BIC - however, BIC is only slightly lower). The p-value is really low (0.002).

  
  
  
*(4) Should we keep (D \| day)?*

```{r, message=FALSE}
no_disturbance_slopes_model = lmer(regional_mean_bioarea ~ 
                                     metaecosystem_type + 
                                     disturbance  + 
                                     (metaecosystem_type | day) +
                                     (1 | system_nr), 
                                   data = ds_regional_MM_SL_t2t7, 
                                   REML = FALSE)

anova(no_interaction_model, no_disturbance_slopes_model)
```

No (according to AIC and BIC - however, AIC is only slightly lower). The p-value is low (0.1785).

  
  
  
*(5) Should we keep (1 \| system_nr)?*

```{r}
no_system_nr = lmer(regional_mean_bioarea ~ 
                      metaecosystem_type + 
                      disturbance  + 
                      (metaecosystem_type | day), 
                    data = ds_regional_MM_SL_t2t7, 
                    REML = FALSE)

anova(no_disturbance_slopes_model, no_system_nr)
```

Yes according to AIC (but no according to BIC). The p-value is low (0.09).

*Should we keep these parameters?*

|    Parameter     |           AIC           |           BIC            |
|:----------------:|:-----------------------:|:------------------------:|
| \| (correlation) |           Yes           |           Yes            |
|      M \* D      |           No            |            No            |
|     (M \| t)     |           Yes           | Yes (but slightly lower) |
|    *(D \| t)*    | No (but slightly lower) |            No            |
|   *(1 \| ID)*    |           Yes           |            No            |

According to AIC, the best model should be M + D + (1 \| system_nr). BIC would take out (1 \| system_nr). But as we are going for AIC here, our best model should include it.

To make sure everything is okay, let's take a look at all our models.

```{r}
anova(full_model_correlated, full_model_uncorrelated, no_interaction_model, no_metaeco_slopes_model, no_disturbance_slopes_model, no_system_nr)
```

Odd, in some of the models chi squared is zero and in some the degrees of freedom are zero.

The best model according to AIC should be M + D + (M \| day) + (1 \| system number) (`no_disturbance_slopes_model`). However, it has zero degrees of freedom.

So, the models I'm going to consider as possible models are the following ones:

-   M + D + (M \| t) + (1 \| ID) [Best model according to AIC]
-   M + D + (M \| t) + (D \| t) + (1 \| ID) [Best model according to AIC with (D \| t), which had a slightly higher AIC]
-   M + D + (M \| t) [Best model according to BIC]
-   M + D [Best model according to BIC without (M \| t), which had only a slightly higher BIC]

```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Create a table with all the models in which time is a random effect. 

### --- INITIALISE TABLE --- ###

columns = c("model", "time_point", "AIC", "BIC", "R2", "R2_fixed", "R2_meta_mixed", "R2_meta_fixed") # "R2_mixed"
random_time_table = data.frame(matrix(ncol = length(columns),
                                     nrow = 0))
colnames(random_time_table) = columns

### --- M + D + (M | t) + (1 | ID) --- ###

for (last_point in 3:7) {
  
  full_model = lmer(regional_mean_bioarea ~ 
                      disturbance +
                      metaecosystem_type +
                      (metaecosystem_type | day) +
                      (1 | system_nr),
                    data = filter(ds_regional_MM_SL_t2t7, 
                                  time_point <= last_point),
                    REML = FALSE,
                    control = lmerControl(optimizer ="Nelder_Mead"))
  
  null_model = lm(regional_mean_bioarea ~ 
                    1 , 
                  data = filter(ds_regional_MM_SL_t2t7, time_point <= last_point))
   
  metaeco_null = lmer(regional_mean_bioarea ~  
                        disturbance  + 
                        (1 | day) +
                        (1 | system_nr),
                                 data = filter(ds_regional_MM_SL_t2t7, 
                                               time_point <= last_point),
                                 REML = FALSE, 
                                 control = lmerControl(optimizer ="Nelder_Mead"))
  
  random_time_table = update_all_models_table("M + D + (M|t) + (1|ID)",
                                             random_time_table, 
                                             full_model, 
                                             null_model,
                                             metaeco_null,
                                             "mixed")
  
}

### --- M + D + (M | t) + (D | t) + (1 | ID) --- ###

for (last_point in 3:7) {
  
  full_model = lmer(regional_mean_bioarea ~ 
                      disturbance +
                      metaecosystem_type +
                      (metaecosystem_type | day) +
                      (disturbance | day) +
                      (1 | system_nr),
                    data = filter(ds_regional_MM_SL_t2t7, 
                                  time_point <= last_point),
                    REML = FALSE,
                    control = lmerControl(optimizer ="Nelder_Mead"))
  
  null_model = lm(regional_mean_bioarea ~ 
                    1 , 
                  data = filter(ds_regional_MM_SL_t2t7, 
                                time_point <= last_point))
  
  metaeco_null = lmer(regional_mean_bioarea ~  
                        disturbance +
                        (disturbance | day) +
                        (1 | system_nr),
                                 data = filter(ds_regional_MM_SL_t2t7, 
                                               time_point <= last_point),
                                 REML = FALSE, 
                                 control = lmerControl(optimizer ="Nelder_Mead"))
  
  random_time_table = update_all_models_table("M + D + (M|t) + (D|t) + (1|ID)",
                                             random_time_table, 
                                             full_model, 
                                             null_model,
                                             metaeco_null,
                                             "mixed")
  
}

### --- M + D + (M  | t) --- ###

for (last_point in 3:7) {
  
  full_model = lmer(regional_mean_bioarea ~ 
                      metaecosystem_type +
                      disturbance +
                      (metaecosystem_type | day),
                    data = filter(ds_regional_MM_SL_t2t7, 
                                  time_point <= last_point),
                    REML = FALSE,
                    control = lmerControl(optimizer ="Nelder_Mead"))
  
  null_model = lm(regional_mean_bioarea ~ 
                    1 , 
                  data = filter(ds_regional_MM_SL_t2t7, time_point <= last_point))
   
  metaeco_null = lm(regional_mean_bioarea ~  
                        disturbance,
                      data = filter(ds_regional_MM_SL_t2t7, 
                                    time_point <= last_point))
  
  random_time_table = update_all_models_table("M + D + (M|t)",
                                             random_time_table, 
                                             full_model, 
                                             null_model,
                                             metaeco_null,
                                             "mixed")
  
}

### --- M + D --- ###

for (last_point in 3:7) {
  
  full_model = lm(regional_mean_bioarea ~ 
                      metaecosystem_type +
                      disturbance,
                    data = filter(ds_regional_MM_SL_t2t7, 
                                  time_point <= last_point))

  null_model = lm(regional_mean_bioarea ~ 
                    1 , 
                  data = filter(ds_regional_MM_SL_t2t7, time_point <= last_point))
   
  metaeco_null = lm(regional_mean_bioarea ~  
                        disturbance,
                      data = filter(ds_regional_MM_SL_t2t7, 
                                    time_point <= last_point))
  
  random_time_table = update_all_models_table("M + D",
                                             random_time_table, 
                                             full_model, 
                                             null_model,
                                             metaeco_null,
                                             "fixed")
  
}

```