---
title: "log_biomass"
author: "Emanuele Giacomuzzo"
date: "2022-08-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

Let's see how linear is the time trend of bioarea and if we can make it more linear with a log10 transformation. We are lucky that during the modelling process we need to drop the first two time points because they were before the first perturbation.

**Linearity of regional bioarea \~ time**

```{r}
ds_regional_biomass %>%
  filter(time_point >= 2) %>%
  ggplot(aes(x = day,
             y = total_regional_bioarea,
             group = day)) +
  geom_boxplot() +
  labs(x = "Day",
       y = "Regional bioarea (µm²)")
```

```{r}
linear_model = lm(total_regional_bioarea ~ 
                    day, 
                  data = ds_regional_biomass %>% 
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"))

par(mfrow=c(2,3))
plot(linear_model, which = 1:5)
```

**Model selection**

Let' start from the full model.

$$
Regional \: bioarea = t + M + D + tM + tD + MD + tDM + (t | system \: nr)
$$

```{r}
full = lmer(total_regional_bioarea ~
                     day * metaecosystem_type * disturbance +
                     (day | system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))
```

*Should we keep the correlation in (day \| system_nr)?*

```{r}
no_correlation = lmer(total_regional_bioarea ~
                     day * metaecosystem_type * disturbance +
                     (day || system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(full, no_correlation)
```

No.

*Should we keep t \* M \* D?*

```{r}
no_threeway = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : metaecosystem_type + 
                     day : disturbance +
                     metaecosystem_type : disturbance + 
                     (day || system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = 'optimx', 
                                         optCtrl = list(method = 'L-BFGS-B')))

anova(no_correlation, no_threeway)
```

No.

*Should we keep t \* M?*

```{r}
no_TM = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : disturbance +
                     metaecosystem_type : disturbance + 
                     (day || system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway,no_TM)
```

Yes.

*Should we keep t \* D?*

```{r}
no_TD = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : metaecosystem_type + 
                     metaecosystem_type : disturbance + 
                     (day || system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway, no_TD)
```

No.

*Should we keep M \* D?*

```{r}
no_MD = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : metaecosystem_type + 
                     (day || system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_TD, no_MD)
```

No.

*Should we keep the random effect of system nr on the time slopes (`day | system_nr)`?*

```{r}
no_random_slopes = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : metaecosystem_type + 
                     (1 | system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_MD, no_random_slopes)
```

No.

**Best model**

Therefore, our best model is:

$$
Regional \: bioarea = t + M + D + tM + (1 | system \: nr) 
$$

The R squared of this model for t2-t7 are:

```{r warning=FALSE}
best_model = no_random_slopes

R2_marginal = r.squaredGLMM(best_model)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(best_model)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

Let's just assume that this model holds also for t2-t5. Then, let's recalculate the R squared.

```{r}
t2_t5 = lmer(total_regional_bioarea ~
                     day +
                     metaecosystem_type +
                     disturbance +
                     day : metaecosystem_type +
                     (day | system_nr),
                     data = ds_regional_biomass %>%
                            filter(time_point >= 2) %>%
                            filter(time_point <= 5) %>%
                            filter(metaecosystem_type == "M_M" | metaecosystem_type == "S_L"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

R2_marginal = r.squaredGLMM(t2_t5)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(t2_t5)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

The R squared of this model for t2-t5 are:

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

[Next steps:]{.underline}

-   [calculating the R2 of the meta-ecosystem type.]{.underline}
