---
title: "small_large_from_isolated"
author: "Emanuele Giacomuzzo"
date: "2022-08-06"
output: html_document
editor_options: 
  chunk_output_type: console
---

##### Tidy

To create the combinations of small and large isolated patches to be compared to the small-large meta-ecosystems, I'm going through the following steps.

1.  Take isolated small and large patches.
2.  Because I had to take out the last
3.  Add them together randomly (here following numeric order, e.g., small isolated 1 with large isolated 11, small isolated 2 with large isolated 12 and so on). Doing this, we make sure that we are matching their disturbances.

```{r message=FALSE, results='hide'}
isolated_S = ds_biomass %>%
  filter(eco_metaeco_type == "S") %>%
  group_by(system_nr, disturbance, time_point, day, patch_size) %>%
  summarise(bioarea_per_volume_across_videos = mean(bioarea_per_volume))

isolated_L = ds_biomass %>%
  filter(eco_metaeco_type == "L") %>%
  group_by(system_nr, disturbance, time_point, day, patch_size) %>%
  summarise(bioarea_per_volume_across_videos = mean(bioarea_per_volume))

### Check that they have the same number of patches, then check which one is the oen missing
length(unique(isolated_S$system_nr))
length(unique(isolated_L$system_nr))
unique(isolated_S$system_nr)
unique(isolated_L$system_nr)

#Take off one of the high disturbance small patches (system nr 50) because isolated small misses one at high disturbance
isolated_L = isolated_L%>%
  filter(!system_nr == 50)

n_isolated_patches = length(unique(isolated_L$system_nr))
n_time_points = 8

number_for_pairing = rep( c( 1:n_isolated_patches), each = n_time_points)
number_for_pairing = as.data.frame(number_for_pairing)
colnames(number_for_pairing) = "number_for_pairing"

isolated_S = cbind(isolated_S, number_for_pairing)
isolated_L = cbind(isolated_L, number_for_pairing)
isolated_S_and_L = rbind(isolated_S, isolated_L)

SL_from_isolated = isolated_S_and_L %>%
  group_by(disturbance, time_point, day, number_for_pairing) %>%
  summarise(regional_mean_bioarea = mean(bioarea_per_volume_across_videos)) %>%
  mutate(metaecosystem_type = "S_L_from_isolated") %>%
  mutate(system_nr = number_for_pairing)

ds_regional_with_SL_from_isolated = rbind(SL_from_isolated, ds_regional)
```

##### Plots

```{r message=FALSE}
ds_regional_with_SL_from_isolated %>%
    filter ( disturbance == "low") %>%
    filter (metaecosystem_type == "S_L" | metaecosystem_type == "S_L_from_isolated") %>%
    ggplot (aes(x = day,
                y = regional_mean_bioarea,
                group = system_nr,
                fill = system_nr,
                color = system_nr,
                linetype = metaecosystem_type)) +
    geom_line () +
    labs(x = "Day", 
         y = "Regional bioarea (something/µl)",
         title = "Disturbance = low",
         fill = "System nr",
         color = "System nr",
         linetype = "") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
    scale_linetype_discrete(labels = c("small-large",
                                     "small-large \n from isolated")) + 
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6)) +
  geom_vline(xintercept = first_perturbation_day, 
             linetype="dotdash", 
             color = "grey", 
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")

ds_regional_with_SL_from_isolated %>%
    filter ( disturbance == "high") %>%
    filter (metaecosystem_type == "S_L" | metaecosystem_type == "S_L_from_isolated") %>%
    ggplot (aes(x = day,
                y = regional_mean_bioarea,
                group = system_nr,
                fill = system_nr,
                color = system_nr,
                linetype = metaecosystem_type)) +
    geom_line () +
    labs(title = "Disturbance = high",
         x = "Day", 
         y = "Regional bioarea (something/µl)",
         fill = "System nr",
         color = "System nr",
         linetype = "") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
    scale_linetype_discrete(labels = c("small-large",
                                     "small-large \n from isolated")) + 
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6)) +
  geom_vline(xintercept = first_perturbation_day, 
             linetype="dotdash", 
             color = "grey", 
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")

ds_regional_with_SL_from_isolated %>%
  filter(disturbance == "low") %>%
  filter(metaecosystem_type == "S_L" | metaecosystem_type == "S_L_from_isolated") %>%
  ggplot(aes(x = day,
             y = regional_mean_bioarea,
             group = interaction(day, metaecosystem_type),
             fill = metaecosystem_type)) +
  geom_boxplot() +
  labs(title = "Disturbance = low",
       x = "Day",
       y = "Regional bioarea (something/microlitre)",
       fill = "") +
  scale_fill_discrete(labels = c("small-large", "isolated small & \n isolated large")) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  geom_vline(xintercept = first_perturbation_day + 0.7, 
             linetype="dotdash", 
             color = "grey", 
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")

ds_regional_with_SL_from_isolated %>%
  filter(disturbance == "high") %>%
  filter(metaecosystem_type == "S_L" | metaecosystem_type == "S_L_from_isolated") %>%
  ggplot(aes(x = day,
             y = regional_mean_bioarea,
             group = interaction(day, metaecosystem_type),
             fill = metaecosystem_type)) +
  geom_boxplot() +
  labs(title = "Disturbance = high",
       x = "Day",
       y = "Regional bioarea (something/microlitre)",
       fill = "") +
  scale_fill_discrete(labels = c("small-large", "isolated small & \n isolated large")) + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  geom_vline(xintercept = first_perturbation_day + 0.7, 
             linetype="dotdash", 
             color = "grey", 
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")
```

##### Modelling

```{r message=FALSE}
mixed_model = lmer(log10(regional_mean_bioarea +1) ~ 
                     day * metaecosystem_type * disturbance +
                     (day | system_nr),
                   data = ds_regional_with_SL_from_isolated %>%
                     filter(metaecosystem_type == "S_L" | 
                              metaecosystem_type == "S_L_from_isolated") %>%
                     filter(time_point >= 2),
                   REML = FALSE,
                   control = lmerControl (optimizer = "Nelder_Mead"))

null_model = lmer(log10(regional_mean_bioarea +1) ~ 
                     day * disturbance +
                     (day | system_nr),
                   data = ds_regional_with_SL_from_isolated %>%
                     filter(metaecosystem_type == "S_L" | 
                              metaecosystem_type == "S_L_from_isolated") %>%
                     filter(time_point >= 2),
                   REML = FALSE,
                   control = lmerControl (optimizer = "Nelder_Mead"))
anova(mixed_model, null_model)
```

##### Tidy again

Let's now create a regional bioarea data-set in which all possible combinations of small-large coupled patches from isolated are created.

```{r}
system_nr_S_low = unique(isolated_S$system_nr)[1:5]
system_nr_L_low = unique(isolated_L$system_nr)[1:5]
system_nr_S_high = unique(isolated_S$system_nr)[6:9]
system_nr_L_high = unique(isolated_L$system_nr)[6:9]

low_pairs = expand.grid(system_nr_S_low,system_nr_L_low)
high_pairs = expand.grid(system_nr_S_high, system_nr_L_high)
pairs = rbind(low_pairs, high_pairs)
number_of_pairs = nrow(pairs)


SL_from_isolated_all_combinations = NULL
for (pair in 1:number_of_pairs){
  
 SL_from_isolated_one_combination = ds_biomass %>%
  filter(system_nr %in% pairs[pair,]) %>%
  group_by(disturbance, day, time_point, system_nr) %>%
  summarise(regional_bioarea_across_videos = mean(bioarea_per_volume)) %>%
  group_by(disturbance, day, time_point) %>%
  summarise(regional_mean_bioarea = mean(regional_bioarea_across_videos)) %>%
  mutate(system_nr = 1000 + pair) %>%
   mutate(metaecosystem_type = "S_L_from_isolated")
 
 SL_from_isolated_all_combinations = rbind(SL_from_isolated_one_combination,
                                          SL_from_isolated_all_combinations)
 
  
}

ds_regional_with_SL_from_isolated = rbind(SL_from_isolated_all_combinations, ds_regional)
```

[Next step: I should try to bootstrap 5 m]{.underline}
