---
title: "S_patches"
author: "Emanuele Giacomuzzo"
date: "2022-08-02"
output: html_document
editor_options:
  chunk_output_type: console
---

##### Plots

```{r small-patches-single-ecosystems-plots}
ds_biomass %>%
  filter(disturbance == "low") %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = culture_ID,
             fill = culture_ID,
             color = culture_ID,
             linetype = eco_metaeco_type)) +
  geom_line(stat = "summary", fun = "mean") +
  labs(x = "Day",
       y = "Local bioarea (µm²/μl)",
       title = "Disturbance = low",
       linetype = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_linetype_discrete(labels = c("small isolated",
                                     "small connected to small",
                                     "small connected to large"))  +
  geom_vline(xintercept = first_perturbation_day,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")

ds_biomass %>%
  filter(disturbance == "high") %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = culture_ID,
             fill = system_nr,
             color = system_nr,
             linetype = eco_metaeco_type)) +
  geom_line(stat = "summary", fun = "mean") +
  labs(title = "Disturbance = high",
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       linetype = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_linetype_discrete(labels = c("small isolated",
                                     "small connected to small",
                                     "small connected to large"))  +
  geom_vline(xintercept = first_perturbation_day,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")
```

```{r small-patches-boxplots}
ds_biomass %>%
  filter(disturbance == "low") %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = interaction(day,eco_metaeco_type),
             fill = eco_metaeco_type)) +
  geom_boxplot() +
  labs(x = "Day",
       y = "Local bioarea (µm²/μl)",
       title = "Disturbance = low",
       fill = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_fill_discrete(labels = c("small isolated",
                                 "small connected to small",
                                 "small connected to large")) +
  geom_vline(xintercept = first_perturbation_day + 0.7,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")

ds_biomass %>%
  filter(disturbance == "high") %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = interaction(day,eco_metaeco_type),
             fill = eco_metaeco_type)) +
  geom_boxplot() +
  labs(title = "Disturbance = high",
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       fill = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_fill_discrete(labels = c("small isolated",
                                 "small connected to small",
                                 "small connected to large")) +
  geom_vline(xintercept = first_perturbation_day + 0.7,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")
```

```{r small-patches-lnRR-plots}
small_patches_publication = 
  ds_biomass_averaged_treatments %>%
  filter(disturbance == "low") %>%
  filter(eco_metaeco_type == "S (S_L)" | eco_metaeco_type == "S (S_S)") %>%
  ggplot(aes(x = day,
             y = lnRR_biomass,
             color = eco_metaeco_type)) +
  geom_point() +
  geom_line(aes(color = eco_metaeco_type)) +
  labs(title = "Disturbance = low",
       x = "Day",
       y = "LnRR Local Bioarea (µm²/μl)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.3, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_color_discrete(labels = c("small connected to small",
                                 "small connected to large")) +
  geom_vline(xintercept = first_perturbation_day + 0.7,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")
small_patches_publication

ds_biomass_averaged_treatments %>%
  filter(disturbance == "high") %>%
  filter(eco_metaeco_type == "S (S_L)" | eco_metaeco_type == "S (S_S)") %>%
  ggplot(aes(x = day,
             y = lnRR_biomass,
             color = eco_metaeco_type)) +
  geom_point() +
  geom_line(aes(color = eco_metaeco_type)) +
  labs(title = "Disturbance = high",
       x = "Day",
       y = "LnRR Local Bioarea (µm²/μl)",
       color = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.3, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_color_discrete(labels = c("small connected to small",
                                 "small connected to large")) +
  geom_vline(xintercept = first_perturbation_day + 0.7,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation")
```

##### Time series

###### Model selection

Let's start from the full model:

$$
ln \: RR (bioarea) = t + P + D + t*P + t*D + P*D
$$

t = time

P = patch type

D = disturbance

And let's consider all data points from the second to the seventh.

```{r choose-time-points}
first_time_point = 2
last_time_point = 7
```

```{r small-patches-full-model}
full_model = lm(lnRR_biomass ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type +
                  day * disturbance + 
                  eco_metaeco_type * disturbance,
                  data = ds_biomass_averaged_treatments %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))
```

*Should we keep t \* P?*

```{r small-patches-no-TM}
no_TM = lm(lnRR_biomass ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * disturbance + 
                  eco_metaeco_type * disturbance,
                  data = ds_biomass_averaged_treatments %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(full_model, no_TM)
```

Yes.

*Should we keep t \* D?*

```{r small-patches-no-TD}
no_TD = lm(lnRR_biomass ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type +
                  eco_metaeco_type * disturbance,
                  data = ds_biomass_averaged_treatments %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(full_model, no_TD)
```

No.

Should we keep P \* D?

```{r small-patches-no-MD}
no_MD = lm(lnRR_biomass ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type,
                  data = ds_biomass_averaged_treatments %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(no_TD, no_MD)
```

No.

###### Best model

Then our best model is:

$$
RR (bioarea) = t + M + D + t*M
$$

Let's then do some model diagnostics.

```{r small-t2-t7-best-model}
best_model = no_MD
par(mfrow = c(2,3))
plot(best_model, which = 1:5)
```

```{r}
R2_full = glance(best_model)$r.squared

no_patch_type = lm(lnRR_biomass ~
                  day + 
                  disturbance,
                  data = ds_biomass_averaged_treatments %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

R2_no_P = glance(no_patch_type)$r.squared
R2_P = R2_full - R2_no_P

R2_full = round(R2_full, digits = 2)
R2_P = round(R2_P, digits = 2)
```

\
The adjusted R squared of the model is `r R2_full` and the adjusted R squared of patch type is `r R2_P` (which includes also its interaction with disturbance).

##### Single time points

[Next step: should I just then report the reponse ratio?]{.underline}

```{r eval = FALSE}
library("ARPobservation")

small_connected = ds_biomass %>%
  filter(eco_metaeco_type == "S (S_S)" | eco_metaeco_type == "S (S_L)") %>%
  filter(time_point == 7) %>%
  filter(disturbance == "low") %>%
  group_by(culture_ID, system_nr, eco_metaeco_type, disturbance,time_point,day) %>%
  summarise(mean_bioarea_per_volume_video_averaged = mean(bioarea_per_volume))

small_isolated = ds_biomass %>%
  filter(eco_metaeco_type == "S") %>%
  filter(time_point == 7) %>%
  filter(disturbance == "low") %>%
  group_by(culture_ID, system_nr, eco_metaeco_type, disturbance,time_point,day) %>%
  summarise(mean_bioarea_per_volume_video_averaged = mean(bioarea_per_volume))

small = rbind(small_connected, small_isolated)

logRespRatio(
  observations = small,
  phase = "eco_metaeco_type",
  base_level = "S",
  conf_level = 0.95,
  bias_correct = TRUE,
  exponentiate = FALSE
)
```
