---
title: "S_patches"
author: "Emanuele Giacomuzzo"
date: "2022-08-02"
output: html_document
editor_options:
  chunk_output_type: console
---

##### Plots

```{r small-patches-single-ecosystems-plots}
for (disturbance_input in c("low", "high")) {

  print(ds_biomass %>%
  filter(disturbance == disturbance_input) %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = culture_ID,
             fill = culture_ID,
             color = culture_ID,
             linetype = eco_metaeco_type)) +
  geom_line(stat = "summary", fun = "mean") +
  labs(title = paste("Disturbance =", disturbance_input),
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       linetype = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_linetype_discrete(labels = c("small isolated",
                                     "small connected to small",
                                     "small connected to large"))  +
  geom_vline(xintercept = first_perturbation_day,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation"))
}
```

```{r small-patches-boxplots}
for (disturbance_input in c("low", "high")) {
  
print(ds_biomass %>%
  filter(disturbance == disturbance_input) %>%
  filter(patch_size == "S") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = interaction(day,eco_metaeco_type),
             fill = eco_metaeco_type)) +
  geom_boxplot() +
  labs(title = paste("Disturbance =", disturbance_input),
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       fill = "") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  scale_fill_discrete(labels = c("small isolated",
                                 "small connected to small",
                                 "small connected to large")) +
  geom_vline(xintercept = first_perturbation_day + 0.7,
             linetype="dotdash",
             color = "grey",
             size=0.7) +
  labs(caption = "Vertical grey line: first perturbation"))
}
```

```{r small-patches-lnRR-plots}
for (disturbance_input in c("low", "high")) {
  
print(ds_lnRR_bioarea_density %>%
  filter(disturbance == disturbance_input) %>%
  filter(eco_metaeco_type == "S (S_S)" | eco_metaeco_type == "S (S_L)") %>%
  ggplot(aes(x = day,
             y = lnRR_bioarea_density,
             color = eco_metaeco_type)) +
  geom_point(position = position_dodge(0.5)) +
  geom_line(position = position_dodge(0.5)) + 
  labs(title = paste("Disturbance =", disturbance_input),
       x = "Day",
       y = "lnRR local bioarea (µm²/µl)",
       color = "") +
  geom_errorbar(aes(ymin = lnRR_lower, 
                    ymax = lnRR_upper), 
                width = .2,
                position = position_dodge(0.5)) + 
  scale_color_discrete(labels = c("small connected to large", 
                                 "small connnected to small")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = c(.40, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)) +
  #geom_vline(xintercept = first_perturbation_day + 0.7, 
  #           linetype="dotdash", 
  #           color = "grey", 
  #           size=0.7) +
  geom_hline(yintercept = 0, 
             linetype="dotted", 
             color = "black", 
             size=0.7))
}
```

##### Time series

###### Model selection

Let's start from the full model (no mixed effect: meta-ecosystems have been pulled to create the lnRR):

$$
ln \: RR (bioarea \: density) = t + P + D + t*P + t*D + P*D
$$

lnRR(bioarea density) = lnRR of the bioarea density (base level is calculated at each disturbance level and time point as the mean bioarea of the small isolated patches)

t = time

P = patch type

D = disturbance

We will exclude in the model the time point 0 and 1. At time point 0 all cultures were the same because that's how we made them. At time point 1 no disturbance event had already taken place.

```{r choose-time-points}
first_time_point = 2
last_time_point = 7
```

```{r small-patches-full-model}
full_model = lm(lnRR_bioarea_density ~                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type +
                  day * disturbance + 
                  eco_metaeco_type * disturbance,
                  data = ds_lnRR %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))
```

*Should we keep t \* P?*

```{r small-patches-no-TM}
no_TP = lm(lnRR_bioarea_density ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * disturbance + 
                  eco_metaeco_type * disturbance,
                  data = ds_lnRR %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(full_model, no_TP)
```

Yes.

*Should we keep t \* D?*

```{r small-patches-no-TD}
no_TD = lm(lnRR_bioarea_density ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type +
                  eco_metaeco_type * disturbance,
                  data = ds_lnRR %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(full_model, no_TD)
```

No.

Should we keep P \* D?

```{r small-patches-no-MD}
no_PD = lm(lnRR_bioarea_density ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day * eco_metaeco_type,
                  data = ds_lnRR %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

AIC(no_TD, no_PD)
```

No.

###### Best model

Then our best model is:

$$
lnRR (bioarea \: density) = t + P + D + t*P
$$

Let's then do some model diagnostics.

```{r small-t2-t7-best-model}
best_model = no_PD
par(mfrow = c(2,3))
plot(best_model, which = 1:5)
```

```{r}
R2_full = glance(best_model)$r.squared
no_patch_type = lm(lnRR_bioarea_density ~
                  day + 
                  disturbance,
                  data = ds_lnRR %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "S (S_S)" | 
                                eco_metaeco_type == "S (S_L)"))

R2_no_P = glance(no_patch_type)$r.squared
R2_P = R2_full - R2_no_P

R2_full = round(R2_full, digits = 2)
R2_P = round(R2_P, digits = 2)
```

\
The adjusted R squared of the model is `r R2_full` and the adjusted R squared of patch type is `r R2_P` (which includes also its interaction with disturbance).

##### Single time points
