---
title: "Untitled"
output: html_document
date: "2024-09-13"
editor_options: 
  chunk_output_type: console
---

UNLIKE ALL THE OTHER ANALYSIS, THIS INCLUDES BOTH DISTURBANCE LEVELS. 

We want to know whether the size of an ecosystem influenced its evaporation rate. We first start from plotting how the water that was added to the cultures changed across size through its mean ± 95 confidence interval:

```{r}

# --- FILTER DATASET --- #

ds_ecosystems_both_disturbances_filtered = ds_ecosystems_both_disturbances %>%
  filter(!is.na(water_addition_ml)) %>%
  mutate(sqrt_water_addition_ml = sqrt(water_addition_ml),
         log_water_addition_ml = log(water_addition_ml),
         inv_water_addition_ml = 1 / water_addition_ml)
```

```{r}

# --- PLOT WATER ADDITION MEAN ± 95 CI --- #

ds_ecosystems_both_disturbances_filtered %>%
  summarySE(measurevar = response_variable,
            groupvars = c("day", "ecosystem_size")) %>%
  ggplot(aes(x = day,
             y = get(response_variable),
             group = interaction(day, ecosystem_size),
             color = ecosystem_size)) +
  geom_point(stat = "summary",
             fun = "mean",
             position = position_dodge(dodging),
             size = treatment_points_size) + 
  geom_line(stat = "summary",
            fun = "mean",
            aes(group = ecosystem_size),
            position = position_dodge(dodging),
            linewidth = treatment_lines_linewidth) +
  geom_errorbar(aes(ymax = get(response_variable) + ci,
                    ymin = get(response_variable) - ci),
                width = width_errorbar,
                position = position_dodge(dodging)) +
  labs(x = "Day",
       y = "Water addition (ml)",
       color = "") +
  scale_x_continuous(breaks = unique(ds_ecosystems$day)) +
  geom_vline(xintercept = resource_flow_days,
             linetype = resource_flow_line_type,
             color = resource_flow_line_colour,
             linewidth = resource_flow_line_width) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = legend_position) +
  scale_color_manual(values = c("#000000", "#737373", "#bdbdbd")) +
  geom_rect(xmin = grey_background_xmin, 
              xmax = grey_background_xmax,
              ymin = grey_background_ymin, 
              ymax = grey_background_ymax, 
              fill = grey_background_fill, 
              alpha = grey_background_alpha,
              color = grey_background_color)
```

<details>
<summary>Single replicates</summary>
```{r}

# --- PLOT WATER ADDITION SINGLE REPLICATES --- #

ds_ecosystems_both_disturbances_filtered %>%
  ggplot(aes(x = day,
             y = get(response_variable),
             group = interaction(culture_ID, day),
             color = ecosystem_size)) +
  geom_point() + 
  geom_line(aes(group = culture_ID)) +
  scale_x_continuous(breaks = unique(ds_ecosystems$day)) +
    theme_bw() +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = legend_position) +
      geom_rect(xmin = grey_background_xmin, 
                xmax = grey_background_xmax,
                ymin = grey_background_ymin, 
                ymax = grey_background_ymax, 
                fill = grey_background_fill, 
                alpha = grey_background_alpha,
                color = grey_background_color) +
  labs(x = "Day",
       y = "Water addition (ml)",
       color = "") +
  scale_color_manual(values = c("#000000", "#737373", "#bdbdbd"))

```
</details>

```{r class.source = "fold-show"}

# --- COMPARE FULL, REDUCED, AND NULL MODEL --- #

full_model = lmer(get(response_variable) ~
                    ecosystem_size +
                    (1 | time_point),
                  data = ds_ecosystems_both_disturbances_filtered,
                  REML = FALSE)

null_model = lmer(get(response_variable) ~
                    (1 | time_point),
                  data = ds_ecosystems_both_disturbances_filtered,
                  REML = FALSE)
```

<br>

<details open="open">
<summary>Full vs null model - ANOVA</summary>
```{r}

# --- FULL VS NULL MODEL - SHOW MODEL STATS --- #

compute.model.stats(full_model,
                    null_model,
                    "mixed_model") %>%
  print()
```
</details>

<details>
<summary>Full model - summary</summary>
```{r}

# --- FULL MODEL - SHOW SUMMARY --- #

print(summary(full_model), digits = 1)
```
</details>

<details>
<summary>Full model - residual plots</summary>

```{r}

# --- FULL MODEL - SHOW RESIDUAL PLOTS --- #

create.res.vs.fit.ecos(ds_ecosystems_both_disturbances_filtered, full_model)
qqnorm(resid(full_model))
qqline(resid(full_model))
```
</details>