---
title: "Untitled"
output:
  html_document:
    code_folding: hide
    profiling: yes
date: "2023-04-14"
editor_options: 
  chunk_output_type: console
---

Our first step in the data analysis involves filtering the data to isolate the relevant data. Specifically, we exclude data points where the response variable couldn’t be computed, as well as time points preceding the initial disturbance and resource flow. Then we plot the data to make sure we filtered data the right way.

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_i)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_i,
                     response_variable)
```

Then, given that we have gathered measurements from the same meta-ecosystem on multiple occasions, we can develop mixed effect models to examine how ecosystem size symmetry influenced this meta-ecosystem variable. To study the effects of ecosystem size symmetry we compare two models to a null model using ANOVA: a full model and a reduced model. In all models, we treat system nr as having a random effect on how the slope and intercept of the relationship between response variable and time, with the slope and intercept being correlated [@Bates2015]. The full model contains the interaction of connection with time (`Response variable ~ symmetry * day + (day | system nr)`), the reduced model contains the connection but without the interaction with time (`Response variable ~ symmetry + day + (day | system nr)`), and the null model doesn't contain the connection at all (`Response variable ~ day + (day | system nr)`).

```{r}
full_model = lmer(
  get(response_variable) ~
    day + 
    ecosystem_size_symmetry +
    ecosystem_size_symmetry : day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead"))

reduced_model = lmer(
  get(response_variable) ~
    day + 
    ecosystem_size_symmetry + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead"))

null_model = lmer(
  get(response_variable) ~
    day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead"))
```

**Full vs null model**

<details open="open">

<summary>Click to view the results of the ANOVA comparison between full and null model</summary>

```{r}
model_stats_full = compute.model.stats(full_model,
                                       null_model,
                                       "mixed_model")

model_stats_full %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```

</details>

<details>

<summary>Click to view the full model output</summary>

```{r}
print(summary(full_model), digits = 1)
```

</details>

<details>

<summary>Click to view the full model residual plots</summary>

```{r}
res_vs_fit = filtered_data %>%
    mutate(predicted = fitted(full_model),
           residuals = resid(full_model)) %>%
    plot_ly(x = ~predicted,
            y = ~residuals,
            type = "scatter",
            mode = "markers",
            marker = list(size = 5, color = "#4C78A8"),
            text = paste(" System nr: ", filtered_data$system_nr, "<br>",
                         "Day: ", filtered_data$day, "<br>",
                         "Meta-ecosystem: ", filtered_data$metaecosystem_type, "<br>",
                         "Tot Biomass: ", round(filtered_data$total_metaecosystem_bioarea_mm2, digits = 0), "<br>"),
            hoverinfo = "text") %>%
    plotly::layout(
        xaxis = list(title = "Fitted Values"),
        yaxis = list(title = "Residuals")
    )
```

```{r}
res_vs_fit
qqnorm(resid(full_model))
```

</details>

<br>

**Reduced vs null model**

<details open="open">

<summary>Click to view the results of the ANOVA comparison between reduced and null model</summary>

```{r}
model_stats_fixed = compute.model.stats(reduced_model,
                                       null_model,
                                       "mixed_model")

model_stats_fixed %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```

</details>

<details>

<summary>Click to view the reduced model output</summary>

```{r}
print(summary(reduced_model), digits = 1)
```

</details>

<details>

<summary>Click to view the reduced model residual plots</summary>

```{r}
res_vs_fit = filtered_data %>%
    mutate(predicted = fitted(reduced_model),
           residuals = resid(reduced_model)) %>%
    plot_ly(x = ~predicted,
            y = ~residuals,
            type = "scatter",
            mode = "markers",
            marker = list(size = 5, color = "#4C78A8"),
            text = paste(" System nr: ", 
                         filtered_data$system_nr, 
                         "<br>",
                         "Day: ", 
                         filtered_data$day, 
                         "<br>",
                         "Meta-ecosystem: ", 
                         filtered_data$metaecosystem_type, 
                         "<br>",
                         "Tot Biomass: ", 
                         round(filtered_data$total_metaecosystem_bioarea_mm2, digits = 0), 
                         "<br>"),
            hoverinfo = "text") %>%
    plotly::layout(xaxis = list(title = "Fitted Values"),
                   yaxis = list(title = "Residuals"))
```

```{r}
res_vs_fit
qqnorm(resid(reduced_model))
```

</details>

```{r echo = FALSE}
results_table = fill.results.table(results_table,
                                   response_variable,
                                   metaecosystem_type_i,
                                   model_stats_full,
                                   model_stats_fixed)
```
