---
title: "Data Regional Biomass"
output: html_document
date: "2022-11-22"
editor_options: 
  chunk_output_type: console
---

-   Each row is a meta-ecosystem.

-   It contains also "fake" meta-ecosystems which I created from unconnected ecosystems (`metaecosystem type = Small-Large unconnected` & `metaecosystem type = Medium-Medium unconnected`).

- Warning appear after the following code, as:
(i) alpha diversity is computed for a culture that is totally crashed, so it has not meaning.
(ii) beta diversity is computed between a culture that is still alive and one that is totally crashed. Because one of the cultures is totally crashed, the Bray-Curtis index is 1.

```{r}

# --- COMPUTE META-ECOSYSTEMS FOR EACH TIME POINT --- #

ds_metaecosystems = NULL
row_i = 0
for (combination_i in 1:n_ecosystems_combinations) {
  for (time_point_selected in time_points) {
    
    row_i = row_i + 1
    
    current_day = sampling_days[time_point_selected + 1]
    current_system_nr = ecos_combin[combination_i, ]$system_nr
    current_combination = ecos_combin[combination_i, ]$ecosystems_combined
    current_disturbance = ecos_combin[combination_i, ]$disturbance
    current_metaeco_type = ecos_combin[combination_i, ]$metaecosystem_type
    current_connection = ecos_combin[combination_i, ]$connection
    current_IDs = c(ecos_combin[combination_i, ]$ID_first_ecosystem,
                    ecos_combin[combination_i, ]$ID_second_ecosystem)
    
    if (current_system_nr %in% metaecosystems_to_take_off)
      next
    
    if (current_IDs[1] == current_IDs[2])
      next
    
    species_vector_two_ecosystems = ds_ecosystems %>%
      filter(time_point == time_point_selected,
             culture_ID %in% current_IDs) %>%
      ungroup() %>%
      select(all_of(protist_species_indiv_per_ml))
    
    absence_presence_two_ecosystems <-
      ifelse(species_vector_two_ecosystems > 0, 1, 0)
    
    #Alpha diversity: Shannon (mean between the two ecosystems)
    
    shannon_ecosystem_1 = diversity(species_vector_two_ecosystems[1, ], index = "shannon")
    shannon_ecosystem_2 = diversity(species_vector_two_ecosystems[2, ], index = "shannon")
    shannon_value = (shannon_ecosystem_1 + shannon_ecosystem_2) / 2
    
    #Alpha diversity: Species richness (mean between the two ecosystems)
    
    richness_ecosystem_1 = specnumber(species_vector_two_ecosystems[1, ])
    richness_ecosystem_2 = specnumber(species_vector_two_ecosystems[2, ])
    mean_richness_value = (richness_ecosystem_1 + richness_ecosystem_2) / 2
    
    #Beta diversity: Jaccard
    
    jaccard_index_value = vegdist(species_vector_two_ecosystems,
                                  method = "jaccard") %>%
      as.numeric()
    
    #Beta diversity: Bray Curtis
    
    bray_curtis_value = vegdist(species_vector_two_ecosystems,
                                method = "bray") %>%
      as.numeric()
    
    #Beta diversity: partitioning of beta diversity from Sorensen index into turnover (Simpson pair-wise dissimilarity) and nestedness (nestedness-fraction of Sorensen)
    
    betapart_core_object = betapart.core(absence_presence_two_ecosystems)
    beta_spatial_turnover_value = beta.pair(betapart_core_object)$beta.sim %>% as.double()
    beta_nestedness_value = beta.pair(betapart_core_object)$beta.sne %>% as.double()
    beta_total_value = beta.pair(betapart_core_object)$beta.sor %>% as.double()
    
    #Gamma diversity: Meta-ecosystem richness
    
    metaecosystem_richness_value = colSums(species_vector_two_ecosystems) %>%
      specnumber()
    
    #Put everything together
    
    ds_metaecosystems[[row_i]] = ds_ecosystems %>%
      filter(culture_ID %in% current_IDs,
             time_point == time_point_selected) %>%
      summarise(total_metaecosystem_bioarea_mm2 = sum(bioarea_tot_mm2),
                total_metaecosystem_Ble_indiv = sum(Ble_tot_indiv),
                total_metaecosystem_Cep_indiv = sum(Cep_tot_indiv),
                total_metaecosystem_Col_indiv = sum(Col_tot_indiv),
                total_metaecosystem_Eug_indiv = sum(Eug_tot_indiv),
                total_metaecosystem_Eup_indiv = sum(Eup_tot_indiv),
                total_metaecosystem_Lox_indiv = sum(Lox_tot_indiv),
                total_metaecosystem_Pau_indiv = sum(Pau_tot_indiv),
                total_metaecosystem_Pca_indiv = sum(Pca_tot_indiv),
                total_metaecosystem_Spi_indiv = sum(Spi_tot_indiv),
                total_metaecosystem_Spi_te_indiv = sum(Spi_te_tot_indiv),
                total_metaecosystem_Tet_indiv = sum(Tet_tot_indiv),
                total_water_addition_ml = sum(water_addition_ml)) %>%
      mutate(system_nr = current_system_nr,
             ecosystems_combined = current_combination,
             metaecosystem_type = current_metaeco_type,
             ecosystem_size_symmetry = case_when(metaecosystem_type == "Small-Large" ~ "asymmetric",
                                                 metaecosystem_type == "Medium-Medium" ~ "symmetric",
                                                 metaecosystem_type == "Small-Small" ~ "symmetric",
                                                 metaecosystem_type == "Large-Large" ~ "symmetric"),
             connection = current_connection,
             disturbance = current_disturbance,
             time_point = time_point_selected,
             day = current_day,
             jaccard_index = jaccard_index_value,
             bray_curtis = bray_curtis_value,
             beta_spatial_turnover = beta_spatial_turnover_value,
             beta_nestedness = beta_nestedness_value,
             beta_total = beta_total_value,
             metaecosystem_richness = metaecosystem_richness_value,
             mean_shannon = shannon_value,
             mean_richness = mean_richness_value) %>%
      ungroup()
    
  }
}

# Tidy up 

ds_metaecosystems = ds_metaecosystems %>%
  bind_rows() %>%
  as.data.frame() %>%
  select(time_point,
         day,
         system_nr,
         ecosystems_combined,
         disturbance,
         metaecosystem_type,
         ecosystem_size_symmetry,
         connection,
         mean_shannon,
         mean_richness,
         jaccard_index,
         bray_curtis,
         beta_spatial_turnover,
         beta_nestedness,
         beta_total,
         metaecosystem_richness,
         total_metaecosystem_bioarea_mm2,
         paste0("total_metaecosystem_", protist_species, "_indiv"),
         total_water_addition_ml)
```

```{r}

# --- TEST CODE --- #

expect_equal(nrow(ds_metaecosystems), 
             n_time_points * n_ecosystems_combinations)
```