---
title: "Biomass analysis (PatchSizePilot)"
author: "Emanuele Giacomuzzo"
date: '2022-07-07'
output: html_document
editor_options: 
  chunk_output_type: console
---

## Local biomass {.tabset .tabset-dropdown}

### All patches {.tabset .tabset-pills}

```{r child = here("r_files", "biomass_local", "sections", "all_patches.Rmd")}
source(here("r_files", "biomass_local", "extracted_sections", "all_patches.R"))
```

### Small patches {.tabset .tabset-pills}

How does biomass density change according to the size to which the patch is connected? *(Does a small patch connected to a small patch have the same biomass density than a small patch connected to a large patch?)*

```{r child = here("r_files", "biomass_local", "sections", "small_patches.Rmd")}
source(here("r_files", "biomass_local", "extracted_sections", "small_patches.R"))
```

### Large patches {.tabset .tabset-pills}

How does biomass density change according to the size to which the patch is connected? *(Does a large patch connected to a large patch have the same biomass density than a large patch connected to a small patch?)*

```{r child = here("r_files", "biomass_local", "sections", "large_patches.Rmd")}
source(here("r_files", "biomass_local", "extracted_sections", "large_patches.R"))
```

### Isolated patches {.tabset .tabset-pills}

How does biomass density change according to the size of isolated patches? *(How does the biomass of small, medium, and large patches change?)*

```{r child = here("r_files", "biomass_local", "sections", "isolated_patches.Rmd")}
source(here("r_files", "biomass_local", "extracted_sections", "isolated_patches.R"))
```
