---
title: "isolated_patches"
author: "Emanuele Giacomuzzo"
date: "2022-08-05"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Isolated patches {.tabset .tabset-pills}

*Research question: how does community abundance change according to the size of isolated patches? (i.e., how does the biomass of small, medium, and large patches change?)*

#### Plots

```{r abundance-isolated-patches-single-ecosystem-plots}
for (disturbance_input in c("low", "high")) {
  print(
    ds_patches %>%
      filter (disturbance == disturbance_input,
              metaecosystem == "no") %>%
      group_by (system_nr, day, patch_size) %>%
      summarise(mean_indiv_per_volume_across_videos = mean(indiv_per_volume)) %>%
      ggplot (
        aes(
          x = day,
          y = mean_indiv_per_volume_across_videos,
          group = system_nr,
          fill = system_nr,
          color = system_nr,
          linetype = patch_size
        )
      ) +
      geom_line () +
      labs(
        title = paste("Disturbance =", disturbance_input),
        x = "Day",
        y = "Community density (individuals/µl)",
        fill = "System nr",
        linetype = ""
      ) +
      scale_colour_continuous(guide = "none") +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      scale_linetype_discrete(
        labels = c("large isolated",
                   "medium isolated",
                   "small isolated")
      )
  )
}
```

```{r abundance-isolated-patches-boxplots}
for (disturbance_input in c("low", "high")) {
  print(
    ds_patches %>%
      filter(disturbance == disturbance_input,
             metaecosystem == "no") %>%
      ggplot(
        aes(
          x = day,
          y = indiv_per_volume,
          group = interaction(day, patch_size),
          fill = patch_size
        )
      ) +
      geom_boxplot() +
      labs(
        title = paste("Disturbance =", disturbance_input),
        x = "Day",
        y = "Community density (individuals/μl)",
        fill = ""
      ) +
      scale_fill_manual(
        values = c(colour_large, colour_medium, colour_small),
        labels = c("Large isolated",
                   "Medium isolated",
                   "Small isolated")
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      )
  )
}
```

#### Model Time Series

We will exclude in the model the time point 0 and 1. At time point 0 all cultures were the same because that's how we made them. At time point 1 no disturbance event had already taken place.

Let's see how linear is the time trend of bioarea and if we can make it more linear with a log10 transformation. We are lucky that during the modelling process we need to drop the first two time points, which would have made the biomass trend not linear.

**Linearity of metaecosystem bioarea \~ time**

```{r abundance-isolated-patches-plot-linearity}
ds_patches %>%
  filter(time_point >= 2) %>%
  ggplot(aes(x = day,
             y = indiv_per_volume,
             group = day)) +
  geom_boxplot() +
  labs(x = "Day",
       y = "Regional bioarea (µm²)")
```

```{r abundance-isolated-patches-linearity-test}
linear_model = lm(indiv_per_volume ~ 
                    day, 
                  data = ds_patches %>% 
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"))

par(mfrow=c(2,3))
plot(linear_model, which = 1:5)
```

**Model selection**

Let' start from the full model.

$$
Local \: Bioarea \: Density = t + P + D + tP + tD + PD + tDP + (t | system \: nr)
$$

```{r abundance-isolated-patches-model-full}
full = lmer(indiv_per_volume ~
                     day * patch_size_volume * disturbance +
                     (day | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))
```

*Should we keep P `(patch_size_volume)`?*

[Need to figure this out.]{.underline}

*Should we keep D `(disturbance)`?*

[Need to figure this out.]{.underline}

*Should we keep the correlation in `(day | system_nr)`?*

```{r abundance-isolated-patches-model-no-correlation}
no_correlation = lmer(indiv_per_volume ~
                     day * patch_size_volume * disturbance +
                     (day || system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(full, no_correlation)
```

No.

*Should we keep the random effect of system nr on the time slopes (`day | system_nr)`?*

```{r abundance-isolated-patches-model-no-random-slopes}
no_random_slopes = lmer(indiv_per_volume ~
                     day * patch_size_volume * disturbance +
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_correlation, no_random_slopes)
```

No.

*Should we keep t \* M \* D?*

```{r abundance-isolated-patches-model-no-threeway}
no_threeway = lmer(indiv_per_volume ~
                     day +
                     patch_size_volume +
                     disturbance +
                     day : patch_size_volume + 
                     day : disturbance +
                     patch_size_volume : disturbance + 
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = 'optimx', 
                                         optCtrl = list(method = 'L-BFGS-B')))

anova(no_random_slopes, no_threeway)
```

No.

*Should we keep t \* M?*

```{r abundance-isolated-patches-model-no-tm}
no_TM = lmer(indiv_per_volume ~
                     day +
                     patch_size_volume +
                     disturbance +
                     day : disturbance +
                     patch_size_volume : disturbance + 
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway,no_TM)
```

Yes.

*Should we keep t \* D?*

```{r abundance-isolated-patches-model-no-td}
no_TD = lmer(indiv_per_volume ~
                     day +
                     patch_size_volume +
                     disturbance +
                     day : patch_size_volume + 
                     patch_size_volume : disturbance + 
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway, no_TD)
```

No.

*Should we keep M \* D?*

```{r abundance-isolated-patches-model-no-md}
no_MD = lmer(indiv_per_volume ~
                     day +
                     patch_size_volume +
                     disturbance +
                     day : patch_size_volume + 
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_TD, no_MD)
```

No.

**Best model**

Therefore, our best model is:

$$
Regional \: bioarea = t + M + D + tM + (1 | system \: nr) 
$$

```{r abundance-isolated-patches-best-model}
best_model = no_MD
```

Let's do some model diagnostics:

```{r abundance-isolated-patches-best-model-residuals}
plot(best_model)
qqnorm(resid(best_model))
```

The R squared of this model for t2-t7 are:

```{r warning=FALSE}
R2_marginal = r.squaredGLMM(best_model)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(best_model)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

The inclusive R squares of this model are:

```{r eval = recompute_analyses}
R2_isolated_patches = partR2(best_model,
                             partvars = c("day", 
                                          "patch_size_volume", 
                                          "disturbance"),
                             R2_type = "conditional", 
                             nboot = 1000, 
                             CI = 0.95)
saveRDS(R2_isolated_patches, file = here("results", "biomass", "R2_isolated_patches.RData"))
```

```{r}
R2_metaecosystem = readRDS(here("results", "biomass", "R2_isolated_patches.RData"))
R2_metaecosystem$IR2
```

Let's just assume that this model holds also for t2-t5. Then, let's recalculate the R squared.

```{r}
t2_t5 = lmer(indiv_per_volume ~
                     day +
                     patch_size_volume +
                     disturbance +
                     day : patch_size_volume + 
                     (1 | system_nr),
                     data = ds_patches %>%
                            filter(time_point >= 2) %>%
                            filter(time_point <= 5) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

plot(t2_t5)
qqnorm(resid(t2_t5))

R2_marginal = r.squaredGLMM(t2_t5)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(t2_t5)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

The R squared of this model for t2-t5 are:

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

The inclusive R squares of this model are:

```{r eval = recompute_analyses}
R2_isolated_patches = partR2(t2_t5,
                             partvars = c("day", 
                                          "patch_size_volume", 
                                          "disturbance"),
                             R2_type = "conditional", 
                             nboot = 1000, 
                             CI = 0.95)
saveRDS(R2_isolated_patches, file = here("results", "R2_isolated_patches_t2t5.RData"))
```

```{r}
R2_metaecosystem = readRDS(here("results", "R2_isolated_patches_t2t5.RData"))
R2_metaecosystem$IR2
```

I could compute the single time points but I don't see the reason why I should do that.
