---
title: "biomass_metaeco_MM_vs_MM_from_isolated"
output: html_document
date: "2022-12-06"
editor_options: 
  chunk_output_type: console
---

#### Biomass

Do a meta-ecosystem with patches of the same size and a meta-ecosystems with patches of different size have different metaecosystem biomass density because of their resource flow? Or would we see this also with small and large ecosystems that are not connected? *(Do the small-large meta-ecosystems have different biomass density from two isolated small and large patches?)*

##### Plots

```{r M_M_from_isolated-single-systems-plots, message=FALSE}
ds_metaecosystems %>%
      filter (disturbance == disturbance_input,
              metaecosystem_type %in% c("M_M", "M_M_from_isolated")) %>%
      ggplot (
        aes(
          x = day,
          y = total_metaecosystem_bioarea,
          group = system_nr,
          fill = system_nr,
          color = system_nr,
          linetype = metaecosystem_type
        )
      ) +
      geom_line () +
      labs(
        x = "Day",
        y = name_y_axis_total_bioarea,
        linetype = ""
      ) +
      scale_linetype_discrete(labels = c(name_MM,
                                          name_MM_from_isolated)) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom"
      ) +
      scale_x_continuous(breaks = unique(ds_metaecosystems$day)) +
      geom_vline(
        xintercept = resource_flow_days[1],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[2],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[3],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[4],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[5],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[6],
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      labs(caption = caption_resource_flow)
```

```{r M_M_from_isolated-single-boxplots}
p_boxplots = ds_metaecosystems %>%
  filter(
    disturbance == disturbance_input,
    metaecosystem_type %in% c("M_M", "M_M_from_isolated")
  ) %>%
  ggplot(
    aes(
      x = day,
      y = total_metaecosystem_bioarea,
      group = interaction(day, metaecosystem_type),
      fill = metaecosystem_type
    )
  ) +
  geom_boxplot(width = boxplot_width) +
  geom_vline(
    xintercept = resource_flow_days[1],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  geom_vline(
    xintercept = resource_flow_days[2],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  geom_vline(
    xintercept = resource_flow_days[3],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  geom_vline(
    xintercept = resource_flow_days[4],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  geom_vline(
    xintercept = resource_flow_days[5],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  geom_vline(
    xintercept = resource_flow_days[6],
    linetype = "dotdash",
    color = "grey",
    size = 0.7
  ) +
  labs(x = "Day",
       y = name_y_axis_total_bioarea,
       fill = "",
       caption = caption_resource_flow) +
  scale_fill_manual(values = c(colour_SL, colour_isolated),
                      labels = c(name_MM, name_MM_from_isolated)) +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    legend.position = "bottom"
  )

p_boxplots
```

```{r}
##Bootstrap from all combinations the p value and delta AIC

system_nr_MM_from_isolated = ds_metaecosystems %>%
  filter(disturbance == disturbance_input,
         metaecosystem_type == "M_M_from_isolated") %>%
  pull(system_nr) %>%
  unique()

n_of_MM_metaecos = ds_metaecosystems %>%
  filter(disturbance == disturbance_input,
         metaecosystem_type == "M_M") %>%
  pull(system_nr) %>%
  unique() %>%
  length()

possible_combinations = combn(system_nr_MM_from_isolated,
                              m = n_of_MM_metaecos) %>%
                        t()

n_subsamples = nrow(possible_combinations)

subsetted_combinations = possible_combinations #There are only 252 possible combinations
```

```{r}
statistics = NULL
for (combination_nr in 1:n_subsamples){
  
  combination = subsetted_combinations[combination_nr,]
  
  filtered_ds = ds_metaecosystems %>%
    filter(disturbance == disturbance_input,
           metaecosystem_type == "M_M" | system_nr %in% combination,
           time_point >= first_time_point_model,
           time_point <= last_time_point_model)
  
  full_model = lmer(
    total_metaecosystem_bioarea ~
      day +
      metaecosystem_type +
      metaecosystem_type : day +
      baseline_bioarea + 
      baseline_bioarea : day +
      (day | system_nr),
    data = filtered_ds,
    REML = FALSE,
    control = lmerControl (optimizer = "Nelder_Mead")
  )
  
  null_model = lmer(
    total_metaecosystem_bioarea ~
      day +
      baseline_bioarea +
      baseline_bioarea : day +
      (day | system_nr),
    data = filtered_ds,
    REML = FALSE,
    control = lmerControl (optimizer = "Nelder_Mead")
  )
  
  anova = anova(full_model, null_model)
  
  p_value = anova$`Pr(>Chisq)`[2]
  
  AIC_full_model = tidy(anova) %>%
    filter(term == "full_model") %>%
    pull(AIC)
  
  AIC_null_model = tidy(anova) %>%
    filter(term == "null_model") %>%
    pull(AIC)
  
  delta_AIC = AIC_full_model - AIC_null_model
  
  statistics[[combination_nr]] = data.frame(p_value = p_value,
                                            delta_AIC = delta_AIC)
  
}

statistics = statistics %>%
  bind_rows()

confidence_interval = 95

percentage_subsamples_to_take_off = 100 - confidence_interval
ratio_subsamples_to_take_off = percentage_subsamples_to_take_off / 100
n_subsamples_to_take_off = n_subsamples * ratio_subsamples_to_take_off

upper_bound = n_subsamples - (n_subsamples_to_take_off / 2) %>%
              ceiling()

lower_bound = 1 + (n_subsamples_to_take_off / 2) %>%
              floor()

p_values = statistics$p_value %>%
  sort(decreasing = TRUE)

delta_AIC_values = statistics$delta_AIC %>%
  sort(decreasing = TRUE)

bootstrapped_statistics = data.frame(
  p_values_mean = mean(p_values),
  p_values_upper_CI = p_values[upper_bound],
  p_values_lower_CI = p_values[lower_bound],
  delta_AIC_mean = mean(delta_AIC_values),
  delta_AIC_upper_CI = delta_AIC_values[upper_bound],
  delta_AIC_lower_CI = delta_AIC_values[lower_bound]
)

bootstrapped_statistics
```

```{r}
p_value = round(bootstrapped_statistics$p_values_mean, digits = 3)
delta_AIC = round(bootstrapped_statistics$delta_AIC_mean, digits = 2)

p_boxplots + 
  labs(title = paste0("p = ", p_value, ", ΔAIC = ", delta_AIC))
```