---
title: "MM vs SL - biomass single points"
output: html_document
date: "2022-12-21"
---

##### Time point 1

Let's start by looking at whether meta-ecosystem type and disturbance had an effect at time point = 1. At this time point, no disturbance event had yet occurred. Therefore, we would not expect an effect of disturbance. In regards to meta-ecosystem type, there might be an effect if it comes from just the sizes of the two ecosystems.

```{r}
chosen_time_point = 1

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_1 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_1
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_1 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 2

```{r}
chosen_time_point = 2

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_2 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_2
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_2 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 3

```{r}
chosen_time_point = 3

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_3 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_3
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_3 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 4

```{r}
chosen_time_point = 4

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_4 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_4
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_4 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 5

```{r}
chosen_time_point = 5

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_5 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_5
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_5 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 6

```{r}
chosen_time_point = 6

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_6 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_6
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_6 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 7

```{r}
chosen_time_point = 7

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_7 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot(width = boxplot_width) +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_7
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_7 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```