---
title: "PatchSize"
html_document:
  toc: yes
  toc_float: yes
  code_folding: hide
  number_sections: yes
  includes:
    after_body: "tabset-dropdown.html"
author: "Emanuele Giacomuzzo"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output:
  html_document:
    code_folding: hide
    profiling: yes
editor_options:
  chunk_output_type: console
---

#  {.tabset}

## Design {.tabset .tabset-pills}

```{r child = here::here("2_analysis", "01_show_design.Rmd")}
```

## Parameters

```{r child = here::here("2_analysis", "02_set_packages.Rmd"), echo = FALSE, message = FALSE, cache = FALSE, autodep = FALSE}
```

```{r child = here("2_analysis", "03_set_functions.Rmd"), echo=FALSE}
```

```{r child = here("2_analysis", "04_set_parameters.Rmd"), class.source = 'fold-show'}
```

## Data {.tabset .tabset-dropdown}

```{r child = here("2_analysis", "05_create_ecos_info.Rmd")}
```

```{r child = here("2_analysis", "06_create_ds_individuals.Rmd")}
```

```{r child = here("2_analysis", "07_create_ds_ecos.Rmd")}
```

```{r child = here("2_analysis", "08_create_ds_ecos_effect_size.Rmd")}
```

```{r child = here("2_analysis", "09_create_ecos_combinations.Rmd")}
```

```{r child = here("2_analysis", "10_create_ecos_combinations_sets.Rmd")}
```

```{r child = here("2_analysis", "11_create_ds_metaecos.Rmd")}
```

```{r child = here("2_analysis", "12_create_ds_classes.Rmd"), eval = FALSE}
```

```{r child = here("2_analysis", "13_create_ds_classes_effect_size.Rmd"), eval = FALSE}
```

## Meta-ecosystems {.tabset .tabset-pills}

```{r}
metaecosystem_type_selected = c("Medium-Medium", "Small-Large")
```

### Alpha {.tabset .tabset-pills}

```{r}
response_variable_selected = "mean_shannon"
```

```{r child = here("2_analysis", "15_analyse_metaecos_variable.Rmd")}
```

### Beta {.tabset .tabset-pills}

```{r}
response_variable_selected = "bray_curtis"
```

```{r child = here("2_analysis", "15_analyse_metaecos_variable.Rmd")}
```

### Gamma {.tabset .tabset-pills}

```{r}
response_variable_selected = "metaecosystem_richness"
```

```{r child = here("2_analysis", "15_analyse_metaecos_variable.Rmd")}
```

### Biomass {.tabset .tabset-pills}

```{r}
response_variable_selected = "total_metaecosystem_bioarea_mm2"
```

```{r child = here("2_analysis", "15_analyse_metaecos_variable.Rmd")}
```

## Ecosystems {.tabset .tabset-pills}

### Shannon {.tabset .tabset-pills}

```{r}
response_variable_selected = "shannon"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### Biomass {.tabset .tabset-pills}

```{r}
response_variable_selected = "bioarea_mm2_per_ml"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### Richness {.tabset .tabset-pills}

```{r}
response_variable_selected = "species_richness"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### Evenness {.tabset .tabset-pills}

```{r}
response_variable_selected = "evenness_pielou"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### Median Size {.tabset .tabset-pills}

```{r}
response_variable_selected = "median_body_area_µm2"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### Auto/Hetero {.tabset .tabset-pills}

```{r}
response_variable_selected = "auto_hetero_ratio"
```

```{r child = here("2_analysis", "16_analyse_ecos_variable.Rmd")}
```

### BEF {.tabset .tabset-pills}

```{r child = here("2_analysis", "17_analyse_ecos_BEF.Rmd")}
```

### Populations

```{r child = here("2_analysis", "18_analyse_ecos_populations.Rmd"), eval = FALSE}
```

## Figures {.tabset .tabset-pills}

### High disturbance

```{r}
disturbance_selected = "high"
```

```{r child = here("2_analysis", "19_save_plot_paper_metaecos.Rmd")}
```

```{r child = here("2_analysis", "20_save_plot_paper_S_L.Rmd")} 
```

```{r child = here("2_analysis", "21_save_plot_paper_M.Rmd")} 
```

```{r child = here("2_analysis", "22_save_plot_paper_unconnected_AH_ratio.Rmd")}
```

<details>
<summary>Figures to present</summary>
```{r child = here("2_analysis", "23_save_plot_present_metaecos.Rmd"), echo = FALSE}
```

```{r child = here("2_analysis", "24_save_plot_present_S_L.Rmd")} 
```
</details>

### Low disturbance

```{r}
disturbance_selected = "low"
```

```{r child = here("2_analysis", "19_save_plot_paper_metaecos.Rmd")}
```

```{r child = here("2_analysis", "20_save_plot_paper_S_L.Rmd")} 
```

```{r child = here("2_analysis", "21_save_plot_paper_M.Rmd")} 
```

```{r child = here("2_analysis", "22_save_plot_paper_unconnected_AH_ratio.Rmd")}
```

<details>
<summary>Figures to present</summary>
```{r child = here("2_analysis", "23_save_plot_present_metaecos.Rmd"), echo = FALSE}
```

```{r child = here("2_analysis", "24_save_plot_present_S_L.Rmd")} 
```
</details>

## Analysis scripts {.tabset .tabset-pills}

### Video analysis

```{r child = here("2_analysis", "26_script_BEMOVI_video_analysis.Rmd"), class.source = "fold-show"}
```

### Species identification

```{r child = here("2_analysis", "27_script_BEMOVI_species_id.Rmd"), class.source = "fold-show"}
```

## Other

```{r child = here("2_analysis", "28_show_other.Rmd")}
```