---
title: "isolated_patches"
author: "Emanuele Giacomuzzo"
date: "2022-08-05"
output: html_document
editor_options: 
  chunk_output_type: console
---

#### Plots

```{r}
ds_biomass_abund %>%
  filter ( disturbance == "low") %>%
  filter(metaecosystem == "no") %>%
  group_by (system_nr, day, patch_size) %>%
  summarise(mean_bioarea_per_volume_across_videos = mean(bioarea_per_volume)) %>%
  ggplot (aes(x = day,
                y = mean_bioarea_per_volume_across_videos,
                group = system_nr,
                fill = system_nr,
              color = system_nr,
                linetype = patch_size)) +
    geom_line () +
    labs(x = "Day", 
         y = "Regional bioarea (µm²/µl)",
         title = "Disturbance = low",
         fill = "System nr",
         linetype = "") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
  scale_colour_continuous(guide = "none") +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6)) +
  scale_linetype_discrete(labels = c("large isolated",
                                     "medium isolated",
                                     "small isolated"))

ds_biomass_abund %>%
  filter ( disturbance == "high") %>%
  filter(metaecosystem == "no") %>%
  group_by (system_nr, day, patch_size) %>%
  summarise(mean_bioarea_per_volume_across_videos = mean(bioarea_per_volume)) %>%
  ggplot (aes(x = day,
                y = mean_bioarea_per_volume_across_videos,
                group = system_nr,
                fill = system_nr,
              color = system_nr,
                linetype = patch_size)) +
    geom_line () +
    labs(x = "Day", 
         y = "Regional bioarea (µm²/µl)",
         title = "Disturbance = low",
         fill = "System nr",
         linetype = "") +
    scale_y_continuous(limits = c(0, 6250)) +
    scale_x_continuous(limits = c(-2, 30)) +
  scale_colour_continuous(guide = "none") +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6)) +
  scale_linetype_discrete(labels = c("large isolated",
                                     "medium isolated",
                                     "small isolated"))
```

```{r}
ds_biomass_abund %>%
  filter(disturbance == "low") %>%
  filter(metaecosystem == "no") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = interaction(day, patch_size),
             fill = patch_size)) +
  geom_boxplot() + 
  labs(title = "Disturbance = low",
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       fill = "") + 
  scale_fill_discrete(labels = c("isolated large", "isolated medium", "isolated small")) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6))

ds_biomass_abund %>%
  filter(disturbance == "high") %>%
  filter(metaecosystem == "no") %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = interaction(day, patch_size),
             fill = patch_size)) +
  geom_boxplot() + 
  labs(title = "Disturbance = high",
       x = "Day",
       y = "Local bioarea (µm²/μl)",
       fill = "") + 
  scale_fill_discrete(labels = c("isolated large", "isolated medium", "isolated small")) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.position = c(.95, .95),
          legend.justification = c("right", "top"),
          legend.box.just = "right",
          legend.margin = margin(6, 6, 6, 6))
```

#### Model Time Series

We will exclude in the model the time point 0 and 1. At time point 0 all cultures were the same because that's how we made them. At time point 1 no disturbance event had already taken place.

Let's see how linear is the time trend of bioarea and if we can make it more linear with a log10 transformation. We are lucky that during the modelling process we need to drop the first two time points, which would have made the biomass trend not linear.

**Linearity of regional bioarea \~ time**

```{r}
ds_biomass_abund %>%
  filter(time_point >= 2) %>%
  ggplot(aes(x = day,
             y = bioarea_per_volume,
             group = day)) +
  geom_boxplot() +
  labs(x = "Day",
       y = "Regional bioarea (µm²)")
```

```{r}
linear_model = lm(bioarea_per_volume ~ 
                    day, 
                  data = ds_biomass_abund %>% 
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"))

par(mfrow=c(2,3))
plot(linear_model, which = 1:5)
```

**Model selection**

Let' start from the full model.

$$
Local \: Bioarea \: Density = t + P + D + tP + tD + PD + tDP + (t | system \: nr)
$$

```{r}
full = lmer(bioarea_per_volume ~
                     day * patch_size * disturbance +
                     (day | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))
```

*Should we keep the correlation in `(day | system_nr)`?*

```{r}
no_correlation = lmer(bioarea_per_volume ~
                     day * patch_size * disturbance +
                     (day || system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(full, no_correlation)
```

No.

*Should we keep the random effect of system nr on the time slopes (`day | system_nr)`?*

```{r}
no_random_slopes = lmer(bioarea_per_volume ~
                     day * patch_size * disturbance +
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_correlation, no_random_slopes)
```

No.

*Should we keep t \* M \* D?*

```{r}
no_threeway = lmer(bioarea_per_volume ~
                     day +
                     patch_size +
                     disturbance +
                     day : patch_size + 
                     day : disturbance +
                     patch_size : disturbance + 
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = 'optimx', 
                                         optCtrl = list(method = 'L-BFGS-B')))

anova(no_random_slopes, no_threeway)
```

No.

*Should we keep t \* M?*

```{r}
no_TM = lmer(bioarea_per_volume ~
                     day +
                     patch_size +
                     disturbance +
                     day : disturbance +
                     patch_size : disturbance + 
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway,no_TM)
```

Yes.

*Should we keep t \* D?*

```{r}
no_TD = lmer(bioarea_per_volume ~
                     day +
                     patch_size +
                     disturbance +
                     day : patch_size + 
                     patch_size : disturbance + 
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_threeway, no_TD)
```

No.

*Should we keep M \* D?*

```{r}
no_MD = lmer(bioarea_per_volume ~
                     day +
                     patch_size +
                     disturbance +
                     day : patch_size + 
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

anova(no_TD, no_MD)
```

No.

**Best model**

Therefore, our best model is:

$$
Regional \: bioarea = t + M + D + tM + (1 | system \: nr) 
$$

```{r}
best_model = no_MD
```

Let's do some model diagnostics:

```{r}
plot(best_model)
qqnorm(resid(best_model))
```

The R squared of this model for t2-t7 are:

```{r warning=FALSE}
R2_marginal = r.squaredGLMM(best_model)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(best_model)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

Let's just assume that this model holds also for t2-t5. Then, let's recalculate the R squared.

```{r}
t2_t5 = lmer(bioarea_per_volume ~
                     day +
                     patch_size +
                     disturbance +
                     day : patch_size + 
                     (1 | system_nr),
                     data = ds_biomass_abund %>%
                            filter(time_point >= 2) %>%
                            filter(time_point <= 5) %>%
                            filter(metaecosystem == "no"),
                   REML = FALSE,
                   control = lmerControl(optimizer = "Nelder_Mead"))

plot(t2_t5)
qqnorm(resid(t2_t5))

R2_marginal = r.squaredGLMM(t2_t5)[1]
R2_marginal = round(R2_marginal, digits = 2)
R2_conditional = r.squaredGLMM(t2_t5)[2]
R2_conditional = round(R2_conditional, digits = 2)
```

The R squared of this model for t2-t5 are:

-   Marginal R2 = `r R2_marginal`

-   Conditional R2 = `r R2_conditional`

```{r eval = FALSE}

### --- Work in progress: calculating R2 of M --- ###

R2_regional = partR2(best_model,
       partvars = c("day", 
                    "patch_size", 
                    "disturbance"),
       R2_type = "marginal", 
       nboot = 1000, 
       CI = 0.95)
saveRDS(R2_regional, file = here("results", "biomass", "R2_regional.RData"))
```

```{r eval = FALSE}
readRDS(here("results", "biomass", "R2_regional.RData"))
```

#### Model Time Points

[I could compute the single time points but I don't see the reason why I should do that.]{.underline}
