---
title: "Untitled"
output:
  html_document:
    code_folding: hide
    profiling: yes
date: "2023-04-14"
editor_options: 
  chunk_output_type: console
---

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_input_model)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_input_model,
                     response_variable)
```

The p-values and ΔAIC of the connection are computed for all possible combinations of the isolated patches, creating a p-value and ΔAIC distributions. We keep as p-value and ΔAIC of the comparison the mean of such distributions.

<details>
  <summary>Click for bootstrapping ΔAIC and p-value</summary>
  
&nbsp;<br>
  
If you see "*Warning in (function (iprint = 0L, maxfun = 10000L, FtolAbs = 1e-05, FtolRel = \## 1e-15, : unused control arguments ignored*", Ignore it. It just means that you didn't pass the control argument to the Nelder_Mead optimiser, so it uses the default.

```{r}
#Compute stats for all patch combinations 
isolated_combinations_sets_filtered =  isolated_combinations_sets %>%
  filter(disturbance == disturbance_global_input,
         metaecosystem_type %in% metaecosystem_type_input_model)

n_sets = isolated_combinations_sets_filtered %>%
  pull(set) %>%
  max()

iterated_results_table = data.frame(
  Response = as.character(NA),
  Levels = as.character(NA),
  ΔAIC_full = NA,
  p_full = NA,
  ΔR2_full = NA,
  ΔAIC_fix = NA,
  p_fix = NA,
  ΔR2_fix = NA,
  combination_set = NA,
  system_nr_isolated_systems = as.character(NA)
) %>%
  slice(-1)

for (set_input in 1:n_sets) {
  
  system_nr_isolated_systems_input = isolated_combinations_sets_filtered %>%
    filter(
      metaecosystem_type %in% metaecosystem_type_input_model,
      connection == "isolated",
      set == set_input
    ) %>%
    pull(system_nr)
  
  filtered_data = ds_metaecosystems %>%
    filter(
      time_point >= first_time_point_model,
      time_point <= last_time_point_model,
      metaecosystem_type %in% metaecosystem_type_input_model,
      connection == "connected" |
        (connection == "isolated" &
           system_nr %in% system_nr_isolated_systems_input)
    )
  
  null_model = lmer(
    get(response_variable) ~
      day +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  full_model = lmer(
    get(response_variable) ~
      day +
      connection +
      connection:day +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  model_stats_full = compute.model.stats(full_model,
                                         null_model,
                                         "mixed_model")
  
  fixed_model = lmer(
    get(response_variable) ~
      day +
      connection +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  model_stats_fixed = compute.model.stats(fixed_model,
                                          null_model,
                                          "mixed_model")
  
  iterated_results_table = fill.results.table(
    iterated_results_table,
    response_variable,
    metaecosystem_type_input_model,
    model_stats_full,
    model_stats_fixed
  )
  
  iterated_results_table$set[nrow(iterated_results_table)] = set_input
  iterated_results_table$system_nr_isolated_systems[nrow(iterated_results_table)] = paste(system_nr_isolated_systems_input, collapse = " ")
}
```
</details> 

&nbsp;<br>
&nbsp;<br>
&nbsp;<br>

<center>[**Full model**]{.underline} [**(with `connection` and `connection : day`)**]{.underline}</center>

<details>
  <summary>Click for ΔAIC and p-value dsitributions</summary>
```{r}
hist(iterated_results_table$ΔAIC_full, main = "Distribution of ΔAIC of the full model.") 
hist(iterated_results_table$p_full, main = "Distribution of p-values of the full model.") 
```
</details> 

```{r}
model_stats_full = data.frame(
  deltaAIC = mean(iterated_results_table$ΔAIC_full),
  p_value = mean(iterated_results_table$p_full),
  R2 = NA
)

model_stats_full %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```

<details>
  <summary>Click for which system nr produced which AIC in the full model</summary>
```{r}
iterated_results_table %>% 
  select(system_nr_isolated_systems,
         ΔAIC_full) %>%
  arrange(ΔAIC_full)
```
</details> 

&nbsp;<br>
&nbsp;<br>
&nbsp;<br>

<center>[**Fixed model**]{.underline} [**(with `connection`)**]{.underline}</center>

<details>
  <summary>Click for ΔAIC and p-value dsitributions</summary>
```{r}
hist(iterated_results_table$ΔAIC_fix, main = "Distribution of ΔAIC of the fixed model.") 
hist(iterated_results_table$p_fix, main = "Distribution of p-values of the fixed model.") 
```
</details> 

```{r}
model_stats_fixed = data.frame(
  deltaAIC = mean(iterated_results_table$ΔAIC_fix),
  p_value = mean(iterated_results_table$p_fix),
  R2 = NA
)

model_stats_fixed %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```

```{r}
results_table = fill.results.table(
    results_table,
    response_variable,
    metaecosystem_type_input_model,
    model_stats_full,
    model_stats_fixed
  )
```