---
title: "Untitled"
output: html_document
date: "2023-11-30"
editor_options: 
  chunk_output_type: console
---

 <br>

###### Filter

```{r}
filtered_data = ds_metaecosystems %>%
  filter(
    metaecosystem_type %in% metaecosystem_type_i,
    time_point >= first_time_point_model,
    time_point <= last_time_point_model,!is.na(!!sym(response_variable))
  )
```

###### Plot filtered data

```{r}
plot.metaecos.points(filtered_data,
                    metaecosystem_type_i,
                    response_variable,
                    legend_rows = 1)
```

<details>

<summary>Replicates</summary>

```{r}
plot.metaecos.replicates(filtered_data,
                           metaecosystem_type_i,
                           response_variable)
```

</details>

<details>

<summary>Raw figure (to make sure lines are labeled correctly)</summary>

```{r}
```

</details>

 <br>

###### Analysis

The p-values and ΔAIC of the connection are computed for all possible combinations of the unconnected patches, creating a p-value and ΔAIC distributions. We keep as p-value and ΔAIC of the comparison the mean of such distributions.

<details>

<summary>Click for bootstrapping ΔAIC and p-value</summary>

 <br>

If you see "*Warning in (function (iprint = 0L, maxfun = 10000L, FtolAbs = 1e-05, FtolRel = \## 1e-15, : unused control arguments ignored*", Ignore it. It just means that you didn't pass the control argument to the Nelder_Mead optimiser, so it uses the default.

```{r}

# Compute stats for all patch combinations 

unconnected_combinations_sets_filtered =  unconnected_combinations_sets %>%
  filter(metaecosystem_type %in% metaecosystem_type_i)

n_sets = unconnected_combinations_sets_filtered %>%
  pull(set) %>%
  max()

iterated_results_table = data.frame(
  Response = as.character(NA),
  Levels = as.character(NA),
  ΔAIC_full = NA,
  p_full = NA,
  ΔR2_full = NA,
  ΔAIC_reduced = NA,
  p_reduced = NA,
  ΔR2_reduced = NA,
  combination_set = NA
) %>%
  slice(-1)

for (set_i in 1 : n_sets) {
  
  system_nrs_in_set_i = unconnected_combinations_sets_filtered %>%
    filter(
      metaecosystem_type %in% metaecosystem_type_i,
      connection == "unconnected",
      set == set_i
    ) %>%
    pull(system_nr)
  
  filtered_data = ds_metaecosystems %>%
    filter(
      time_point >= first_time_point_model,
      time_point <= last_time_point_model,
      metaecosystem_type %in% metaecosystem_type_i,
      connection == "connected" |
        (connection == "unconnected" & system_nr %in% system_nrs_in_set_i)
    )
  
  null_model = lmer(
    get(response_variable) ~
      day +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  full_model = lmer(
    get(response_variable) ~
      day +
      connection +
      connection:day +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  model_stats_full = compute.model.stats(full_model,
                                         null_model,
                                         "mixed_model")
  
  reduced_model = lmer(
    get(response_variable) ~
      day +
      connection +
      (day | system_nr),
    data = filtered_data,
    REML = FALSE,
    control = lmerControl(optimizer = optimizer_input,
                          optCtrl = list(method = method_input))
  )
  
  model_stats_reduced = compute.model.stats(reduced_model,
                                          null_model,
                                          "mixed_model")
  
  # Here I want to fill 
  
  iterated_results_table = fill.iterated.results.table(
    iterated_results_table = iterated_results_table,
    response_variable = response_variable,
    patch_or_metaecosystem_type_i = metaecosystem_type_i,
    model_stats_full = model_stats_full,
    model_stats_reduced = model_stats_reduced
  )
  
  iterated_results_table$set[nrow(iterated_results_table)] = set_i
  iterated_results_table$system_nr_unconnected_systems[nrow(iterated_results_table)] = paste(system_nrs_in_set_i, collapse = " ")
}
```

Full model

```{r}
hist(iterated_results_table$ΔAIC_full, main = "Distribution of ΔAIC of the full model.") 
hist(iterated_results_table$p_full, main = "Distribution of p-values of the full model.")

model_stats_full = data.frame(
  deltaAIC = mean(iterated_results_table$ΔAIC_full),
  p_value = mean(iterated_results_table$p_full),
  R2 = NA
)
```

Reduced model

```{r}
hist(iterated_results_table$ΔAIC_reduced, main = "Distribution of ΔAIC of the reduced model.") 
hist(iterated_results_table$p_reduced, main = "Distribution of p-values of the reduced model.")

model_stats_reduced = data.frame(
  deltaAIC = mean(iterated_results_table$ΔAIC_reduced),
  p_value = mean(iterated_results_table$p_reduced),
  R2 = NA
)
```

</details>

 <br>

###### Results

Full model

```{r}
model_stats_full %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```

Reduced model

```{r}
model_stats_reduced %>%
  mutate(deltaAIC = round(deltaAIC, digits = 1),
         p_value = round(p_value, digits = 3),
         R2 = NULL,
         evidence = "",
         evidence = ifelse(p_value > 0.1, 
                           "none",
                           evidence),
         evidence = ifelse(p_value < 0.1, 
                           "* weak",
                           evidence),
         evidence = ifelse(p_value < 0.05, 
                           "** moderate",
                           evidence),
         evidence = ifelse(p_value < 0.01, 
                           "*** strong",
                           evidence),
         evidence = ifelse(p_value < 0.001, 
                           "**** very strong",
                           evidence),
         p_value = ifelse(p_value < 0.001,
                           "< 0.001",
                           p_value)) %>%
  print()
```
