---
title: "large_patches"
author: "Emanuele Giacomuzzo"
date: "2022-08-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Large patches {.tabset .tabset-pills}

*Research question: how does biomass density change according to the size to which the patch is connected? (i.e., does a large patch connected to a large patch have the same biomass density than a large patch connected to a small patch?)*

#### Plots

```{r large-single-patches-plots}
for (disturbance_input in c("low", "high")) {
  print(
    ds_biomass_abund %>%
      filter(disturbance == disturbance_input) %>%
      filter(patch_size == "L") %>%
      ggplot(
        aes(
          x = day,
          y = bioarea_per_volume,
          group = system_nr,
          fill = system_nr,
          color = system_nr,
          linetype = eco_metaeco_type
        )
      ) +
      geom_line(stat = "summary", fun = "mean") +
      labs(
        x = "Day",
        y = "Local bioarea (µm²/μl)",
        title = paste("Disturbance =", disturbance_input),
        linetype = ""
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      scale_linetype_discrete(
        labels = c(
          "Large isolated",
          "Large connected to large",
          "Large connected to small"
        )
      ) +
      geom_vline(
        xintercept = first_perturbation_day,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      labs(caption = "Vertical grey line: first perturbation")
  )
}
```

```{r large-patches-boxplots}
for (disturbance_input in c("low", "high")) {
  print(
    ds_biomass_abund %>%
      filter(disturbance == disturbance_input,
             patch_size == "L") %>%
      ggplot(
        aes(
          x = day,
          y = bioarea_per_volume,
          group = interaction(day, eco_metaeco_type),
          fill = eco_metaeco_type
        )
      ) +
      geom_boxplot() +
      labs(
        title = paste("Disturbance =", disturbance_input),
        x = "Day",
        y = "Local bioarea (µm²/μl)",
        fill = ""
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.95, .95),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      scale_fill_manual(
        values = c(colour_isolated, colour_same_size, colour_different_size),
        labels = c(
          "Large isolated",
          "Large connected to large",
          "Large connected to small"
        )
      ) +
      geom_vline(
        xintercept = first_perturbation_day + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      labs(caption = "Vertical grey line: first perturbation")
  )
}
```

```{r large-patches-effect-size-plots}
for (disturbance_input in c("low", "high")) {
  print(
    ds_patches_averaged %>%
      filter(!time_point == 0) %>% #At time point 0 all cultures were the same
      filter(disturbance == disturbance_input) %>%
      filter(eco_metaeco_type == "L (L_L)" |
               eco_metaeco_type == "L (S_L)") %>%
      ggplot(
        aes(x = day,
            y = bioarea_per_volume_d,
            color = eco_metaeco_type)
      ) +
      geom_point(position = position_dodge(0.5)) +
      geom_line(position = position_dodge(0.5)) +
      labs(
        title = paste("Disturbance =", disturbance_input),
        x = "Day",
        y = "hedge's d local bioarea",
        color = ""
      ) +
      #geom_errorbar(aes(ymin = lnRR_lower,
      #                  ymax = lnRR_upper),
      #              width = .2,
      #              position = position_dodge(0.5)) +
      scale_color_discrete(
        labels = c("Large connected to large",
                   "Large connnected to small")
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(.90, .97),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      #  geom_vline(xintercept = first_perturbation_day + 0.7,
      #             linetype="dotdash",
      #             color = "grey",
      #             size=0.7) +
      geom_hline(
        yintercept = 0,
        linetype = "dotted",
        color = "black",
        size = 0.7
      )
  )
}
```

#### Time series

##### Model selection

We will exclude in the model the time point 0 and 1. At time point 0 all cultures were the same because that's how we made them. At time point 1 no disturbance event had already taken place.

```{r choose-time-points-large}
first_time_point = 2
last_time_point = 7
```

Let's start from the full model (no mixed effect: meta-ecosystems have been pulled to create the lnRR):

$$
ln \: RR (bioarea \: density) = t + P + D + t*P + t*D + P*D
$$

lnRR(bioarea density) = lnRR of the bioarea density (base level is calculated at each disturbance level and time point as the mean bioarea of the small isolated patches)

t = time

P = patch type

D = disturbance

```{r large-patches-full-model}
full_model = lm(bioarea_per_volume_d ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day : eco_metaeco_type +
                  day : disturbance + 
                  eco_metaeco_type : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))
```

*Should we keep P?*

```{r large-patches-no_P}
no_P = lm(bioarea_per_volume_d ~
                  day + 
                  disturbance +
                  day : eco_metaeco_type +
                  day : disturbance + 
                  eco_metaeco_type : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

AIC(full_model, no_P)
```

Let's see.

*Should we keep D?*

```{r large-patches-no_D}
no_D = lm(bioarea_per_volume_d ~
                  day + 
                  eco_metaeco_type + 
                  day : eco_metaeco_type +
                  day : disturbance + 
                  eco_metaeco_type : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

AIC(full_model, no_D)
```

Let's see.

*Should we keep t \* P?*

```{r large-patches-no-TM}
no_TP = lm(bioarea_per_volume_d ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day : disturbance + 
                  eco_metaeco_type : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

AIC(full_model, no_TP)
```

No.

*Should we keep t \* D?*

```{r large-patches-no-TD}
no_TD = lm(bioarea_per_volume_d ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  eco_metaeco_type : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

AIC(no_TP, no_TD)
```

Yes.

Should we keep P \* D?

```{r large-patches-no-PD}
no_PD = lm(bioarea_per_volume_d ~
                  day + 
                  eco_metaeco_type + 
                  disturbance +
                  day : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

AIC(no_TP, no_PD)
```

No.

##### Best model

Then our best model is:

$$
lnRR (bioarea \: density) = t + P + D + tP
$$

Let's then do some model diagnostics.

```{r large-t2-t7-best-model}
best_model = no_PD
par(mfrow = c(2,3))
plot(best_model, which = 1:5)
```

```{r}
R2_full = glance(best_model)$r.squared

no_patch_type = lm(bioarea_per_volume_d ~
                  day + 
                  disturbance +
                  day : disturbance,
                  data = ds_patches_averaged %>%
                         filter(time_point >= first_time_point) %>%
                         filter(time_point <= last_time_point) %>%
                         filter(eco_metaeco_type== "L (L_L)" | 
                                eco_metaeco_type == "L (S_L)"))

R2_no_P = glance(no_patch_type)$r.squared
R2_P = R2_full - R2_no_P

R2_full = round(R2_full, digits = 2)
R2_P = round(R2_P, digits = 2)
```

\
The adjusted R squared of the model is `r R2_full` and the adjusted R squared of patch type is `r R2_P` (which includes also its interaction with disturbance).

Single time points: see modelling choices.
