---
title: "evaporation_tests"
author: "Emanuele Giacomuzzo"
date: "2022-08-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

### Evaporation when microwaving 15 falcon tubes at the time

To quantify the amount of evaporation incurred by the cultures, I conducted weight measurements before and after microwaving for three minutes. Initially, I weighed 15 falcon tubes, then added deionised water to each tube before re-weighing them to determine the initial water weight. Subsequently, the 15 falcon tubes were placed inside a tube rack and microwaved for three minutes. After microwaving, I assessed the remaining water volume in each tube using a beaker. This process was repeated for both 5.25 ml (low disturbance) and 6.75 ml (high disturbance) deionised water volumes, across three sets of 15 tubes for each disturbance level.

```{r, class.source = 'fold-hide'}
evaporation.test = read.csv(here("data", "evaporation_test","evaporation_test_right.csv"), header = TRUE)

evaporation.test %>%
  ggplot(aes (x = as.character(water_pipetted),
                y = weight_water_evaporated,
                group = interaction(water_pipetted, as.character(rack)),
                fill = as.character(rack))) +
  geom_boxplot(width = boxplot_width) +
  labs(x = "Water volume (ml)" , 
       y = "Evaporation (g)", 
       fill = "Rack replicate")
```

### Evaporation when microwaving 5 tubes with 10 filled or empty tubes

To assess the extent of evaporation in the presence of varying tube conditions, I conducted weight measurements before and after microwaving five falcon tubes under two distinct treatments: one with ten additional filled tubes and another with ten empty tubes. Initially, I weighed 15 falcon tubes for each treatment, then added 6.75 ml of deionized water to either just five of them or to all of them, before re-weighing to ascertain the water weight. Subsequently, each set of 15 falcon tubes was placed inside a tube rack and microwaved for three minutes. Following microwaving, I evaluated the remaining water volume in each tube using a beaker.

```{r, class.source = 'fold-hide'}
evaporation.test = read.csv(here("data", "evaporation_test", "evaporation_test_fill_nofill.csv"), header = TRUE)

evaporation.test %>%
  ggplot(aes (x = all_tubes_water,
              y = weight_water_evaporated)) +
  geom_boxplot(width = boxplot_width) +
  labs(x = "Water in the other 10 tubes" , 
  y = "Evaporation (g)")
```
