---
title: "Water evaporation (PatchSizePilot)"
author: "Emanuele Giacomuzzo"
date: '2022-07-13'
output: html_document
editor_options: 
  chunk_output_type: console
---

### Effects of evaporation 

We want to know if there was a systematic bias in the evaporation of different treatments (disturbance, patch size) and whether evaporation changed across time. My expectation would be that we would see a difference among the exchanges 2,3 and the exchanges 4,5,6. This is because in exchange 2,3 cultures were microwaved in 15 tubes for 3 minutes and in exchange 4,5,6 cultures were microwaved in 4 tubes for only 1 minute.

#### Tidy

```{r tidy-evaporation-effects-on-biomass}

#Columns: exchange & evaporation
ds_for_evaporation = gather(ds_for_evaporation, 
                            key = exchange, 
                            value = evaporation, 
                            water_add_after_t2:water_add_after_t6)
ds_for_evaporation[ds_for_evaporation == "water_add_after_t2"] = "2"
ds_for_evaporation[ds_for_evaporation == "water_add_after_t3"] = "3"
ds_for_evaporation[ds_for_evaporation == "water_add_after_t4"] = "4"
ds_for_evaporation[ds_for_evaporation == "water_add_after_t5"] = "5"
ds_for_evaporation[ds_for_evaporation == "water_add_after_t6"] = "6"
ds_for_evaporation$evaporation[ds_for_evaporation$exchange == 2] = ds_for_evaporation$evaporation[ds_for_evaporation$exchange == 2] / 2 #This is because exchange contained the topping up of two exchanges
ds_for_evaporation$evaporation[ds_for_evaporation$exchange == 2] = ds_for_evaporation$evaporation[ds_for_evaporation$exchange == 2] + 2 #We need to add 2 ml to the evaporation that happened at the exchange events 1 and 2. This is because we already added 1 ml of water at exchange 1 and 1 ml of water at exchange 2. 

#Column: nr_of_tubes_in_rack
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 1] = 15
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 2] = 15
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 3] = 15
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 4] = 4
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 5] = 4
ds_for_evaporation$nr_of_tubes_in_rack[ds_for_evaporation$exchange == 6] = 4
```

#### Plot

```{r plot, warning = FALSE}
ds_for_evaporation %>%
  filter(disturbance == disturbance) %>%
  ggplot(aes(x = as.character(nr_of_tubes_in_rack),
             y = evaporation)) + 
  geom_boxplot() + 
  labs(x = "Number of tubes in rack", 
       y = "Evaporation (ml)")

ds_for_evaporation %>%
  filter(disturbance == disturbance) %>%
  ggplot(aes(x = as.character(patch_size),
             y = evaporation)) + 
  geom_boxplot() + 
  labs(x = "Patch size", 
       y = "Evaporation (ml)")

ds_for_evaporation %>%
  filter(disturbance == disturbance) %>%
  ggplot(aes(x = as.character(day),
             y = evaporation)) + 
  geom_boxplot() + 
  labs(x = "Day", 
       y = "Evaporation (ml)")

ds_for_evaporation %>%
  filter(disturbance == disturbance) %>%
  ggplot(aes(x = disturbance,
             y = evaporation)) + 
  geom_boxplot() + 
  labs(x = "Disturbance", 
       y = "Evaporation (ml)")
```

It seems like there is no real difference across time, disturbance, or patch type. However, we could also run a mixed effect model to show that they do not.

#### Mixed effect model

[It gives me the following error:]{.underline}

-   *Error in fn(nM\$xeval()) : Downdated VtV is not positive definite*

```{r mixed model, eval = FALSE}

mixed.model = lmer(evaporation  ~ 
                     patch_size * disturbance  * exchange + 
                     (exchange | culture_ID), 
                   data = ds_for_evaporation,
                   REML = FALSE, 
                   control = lmerControl (optimizer = "Nelder_Mead"))

null.model = lm(evaporation ~
                  1, 
                data = ds_for_evaporation)

anova(mixed.model, null.model)
```
