---
title: "PhD Chapter 1 - PatchSize"
author: "Emanuele Giacomuzzo"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
bibliography: library.bib
html_document:
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
    includes:
      after_body: tabset-dropdown.html
editor_options: 
  chunk_output_type: console
---

#  {.tabset}

```{r}
library(here)
start_time = Sys.time()
```

```{r child = here("r_files", "packages.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "functions.Rmd"), echo = FALSE}
```

```{r child = here("r_files", "parameters.Rmd"), echo = FALSE}
```

## Overview {.tabset .tabset-pills}

```{r overview-experiment, child = here("r_files", "overview.Rmd"), eval = compute_n_display_datasets}
```

## Data {.tabset .tabset-dropdown}

```{r child = here("r_files", "data_culture_info.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_patches.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_patches_effect_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_metaecosystems.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_individuals.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_median_body_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_median_body_size_effect_size.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_classes.Rmd"), eval = compute_n_display_datasets}
```

```{r child = here("r_files", "data_classes_effect_size.Rmd"), eval = compute_n_display_datasets}
```

## Meta-ecosystems {.tabset .tabset-dropdown}

### All

```{r child = here("r_files", "all_metaecos_biomass.Rmd")}
```

```{r child = here("r_files", "all_metaecos_beta_diversity.Rmd")}
```

### Equally sized {.tabset .tabset-pills}

```{r child = here("r_files", "equally_sized_metaecos_biomass.Rmd")}
```

```{r child = here("r_files", "equally_sized_metaecos_beta_diversity.Rmd")}
```

```{r child = here("r_files", "equally_sized_metaecos_gamma_diversity.Rmd")}
```

### MM vs SL (meta-ecosystems and isolated) {.tabset .tabset-pills}

```{r child = here("r_files", "MM_all_vs_SL_all_biomass.Rmd")}
```

```{r child = here("r_files", "MM_all_vs_SL_all_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "MM_all_vs_SL_all_beta_diversity.Rmd")}
```

```{r child = here("r_files", "MM_all_vs_SL_all_gamma_diversity.Rmd")}
```

## Patches {.tabset .tabset-dropdown}

### All {.tabset .tabset-pills}

```{r child = here("r_files", "all_patches_biomass.Rmd"), eval = include_non_clean_scripts}
```

### Isolated {.tabset .tabset-pills}

```{r child = here("r_files", "isolated_patches_biomass.Rmd")}
```

```{r child = here("r_files", "isolated_patches_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "isolated_patches_species_densities.Rmd")}
```

```{r child = here("r_files", "isolated_patches_species_dominance.Rmd")}
```

```{r child = here("r_files", "isolated_patches_species_composition.Rmd")}
```

```{r child = here("r_files", "isolated_patches_body_size_distribution.Rmd")}
```

```{r child = here("r_files", "isolated_patches_size_classes.Rmd")}
```

### Small {.tabset .tabset-pills}

```{r child = here("r_files", "small_patches_biomass.Rmd")}
```

```{r child = here("r_files", "small_patches_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "small_patches_species_densities.Rmd")}
```

```{r child = here("r_files", "small_patches_median_body_size.Rmd")}
```

```{r child = here("r_files", "small_patches_body_size_distribution.Rmd")}
```

```{r child = here("r_files", "small_patches_size_classes.Rmd")}
```

### Medium {.tabset .tabset-pills}

```{r child = here("r_files", "medium_patches_biomass.Rmd")}
```

```{r child = here("r_files", "medium_patches_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "medium_patches_species_densities.Rmd"), eval = include_non_clean_scripts}
```

### Large {.tabset .tabset-pills}

```{r child = here("r_files", "large_patches_biomass.Rmd")}
```

```{r child = here("r_files", "large_patches_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "large_patches_species_densities.Rmd")}
```

```{r child = here("r_files", "large_patches_body_size_distribution.Rmd")}
```

```{r child = here("r_files", "large_patches_median_body_size.Rmd")}
```

```{r child = here("r_files", "large_patches_size_classes.Rmd")}
```

### SL {.tabset .tabset-pills}

```{r child = here("r_files", "SL_biomass.Rmd")}
```

```{r child = here("r_files", "SL_alpha_diversity.Rmd")}
```

```{r child = here("r_files", "SL_species_densities.Rmd")}
```

```{r child = here("r_files", "SL_species_dominance.Rmd")}
```

```{r child = here("r_files", "SL_species_composition.Rmd")}
```

```{r child = here("r_files", "SL_size_classes.Rmd")}
```

## Productivity drivers {.tabset .tabset-pills}

```{r child = here("r_files", "relationship_productivity_richness.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_shannon.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_evenness.Rmd")}
```

```{r child = here("r_files", "relationship_productivity_dominance.Rmd")}
```

## Evaporation {.tabset .tabset-dropdown}

```{r child = here("r_files", "evaporation.Rmd")}
```

```{r child = here("r_files", "evaporation_tests.Rmd")}
```

## Video analysis script

```{r child = here("r_files", "video_analysis_script.Rmd"), class.source = "fold-show"}
```

## Paper

```{r child = here("r_files", "paper.Rmd")}
```

## Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time
```

## Other

In the .bib file get rid of:

-   book_section

-   computer_program

-   web_page

## Bibliography
