---
title: "All MM and SL"
output: html_document
date: "2022-12-13"
editor_options: 
  chunk_output_type: console
---

```{r}
response_variable = "total_metaecosystem_bioarea_mm2"
```

##### Means {.tabset .tabset-pills}

```{r}
p_MM_SL_metaecos_biomass = plot.metaecos.points(ds_metaecosystems, 
                                                metaecosystem_type_input,
                                                response_variable) %>%
  print()
```

###### Small-Large meta-ecosystems vs Small-Large isolated

```{r}
metaecosystem_type_input_model = c("Small-Large meta-ecosystem",
                                   "Small-Large isolated")
```

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_input_model)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_input_model,
                     response_variable)
```

**Construct the full model**

```{r}
full_model = lmer(
  get(response_variable) ~
    day + 
    connection +
    connection : day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

# Calculate the VIF for each predictor variable
#car::vif(full_model)

summary(full_model)
plot(full_model)
qqnorm(resid(full_model))
```

**Test the effects of `connection` and `connection:day`**

```{r}
null_model = lmer(
  get(response_variable) ~
    day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

summary(null_model)
plot(null_model)
qqnorm(resid(null_model))
model_stats = compute.model.stats(full_model,
                    null_model,
                    "mixed_model")

model_stats

results_table = fill.results.table(results_table,
                                   response_variable,
                                   metaecosystem_type_input_model,
                                   model_stats)
```

###### Medium-Medium meta-ecosystem vs MM from isolated

```{r}
metaecosystem_type_input_model = c("Medium-Medium meta-ecosystem",
                                   "Medium-Medium isolated")
```

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_input_model)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_input_model,
                     response_variable)
```

**Construct the full model**

```{r}
full_model = lmer(
  get(response_variable) ~
    day + 
    connection +
    connection : day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

# Calculate the VIF for each predictor variable
#car::vif(full_model)

summary(full_model)
plot(full_model)
qqnorm(resid(full_model))
```

**Test the effects of `connection` and `connection:day`**

```{r}
null_model = lmer(
  get(response_variable) ~
    day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

summary(null_model)
plot(null_model)
qqnorm(resid(null_model))
model_stats = compute.model.stats(full_model,
                    null_model,
                    "mixed_model")

model_stats

results_table = fill.results.table(results_table,
                                   response_variable,
                                   metaecosystem_type_input_model,
                                   model_stats)
```

###### Small-Large meta-ecosystem vs Medium-Medium meta-ecosystem

```{r}
metaecosystem_type_input_model = c("Small-Large meta-ecosystem",
                                   "Medium-Medium meta-ecosystem")
```

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_input_model)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_input_model,
                     response_variable)
```

**Construct the full model**

```{r}
full_model = lmer(
  get(response_variable) ~
    day + 
    patch_size_symmetry +
    patch_size_symmetry : day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

# Calculate the VIF for each predictor variable
#car::vif(full_model)

summary(full_model)
plot(full_model)
qqnorm(resid(full_model))
```

**Test the effects of `patch_size_symmetry` and `patch_size_symmetry:day`**

```{r}
null_model = lmer(
  get(response_variable) ~
    day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

summary(null_model)
plot(null_model)
qqnorm(resid(null_model))
model_stats = compute.model.stats(full_model,
                    null_model,
                    "mixed_model")

model_stats

results_table = fill.results.table(results_table,
                                   response_variable,
                                   metaecosystem_type_input_model,
                                   model_stats)
```

###### SL from isolated vs MM from isolated

```{r}
metaecosystem_type_input_model = c("Medium-Medium isolated",
                                   "Small-Large isolated")
```

```{r}
filtered_data = ds_metaecosystems %>%
                         filter(time_point >= first_time_point_model,
                                time_point <= last_time_point_model,
                                metaecosystem_type %in% metaecosystem_type_input_model)
```

```{r}
plot.metaecos.points(filtered_data,
                     metaecosystem_type_input_model,
                     response_variable)
```

**Construct the full model**

```{r}
full_model = lmer(
  get(response_variable) ~
    day + 
    patch_size_symmetry +
    patch_size_symmetry : day + 
    (day | system_nr), 
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

# Calculate the VIF for each predictor variable
#car::vif(full_model)

summary(full_model)
plot(full_model)
qqnorm(resid(full_model))
```

**Test the effects of `patch_size_symmetry` and `patch_size_symmetry:day`**

```{r}
null_model = lmer(
  get(response_variable) ~
    day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

summary(null_model)
plot(null_model)
qqnorm(resid(null_model))
model_stats = compute.model.stats(full_model,
                    null_model,
                    "mixed_model")

model_stats

results_table = fill.results.table(results_table,
                                   response_variable,
                                   metaecosystem_type_input_model,
                                   model_stats)
```

##### Boxplots

```{r}
plot.metaecos.boxplots(ds_metaecosystems,
                       metaecosystem_type_input,
                       response_variable)
```