---
title: "MM_SL_plots"
author: "Emanuele Giacomuzzo"
date: "2022-08-04"
output: html_document
editor_options: 
  chunk_output_type: console
---

#### Biomass {.tabset .tabset-pills}

```{r}
ds_metaecosystems %>%
      filter (disturbance == disturbance_input,
              metaecosystem_type %in% c("S_L", "M_M")) %>%
      ggplot (
        aes(
          x = day,
          y = total_metaecosystem_bioarea,
          group = system_nr,
          fill = system_nr,
          color = system_nr,
          linetype = metaecosystem_type
        )
      ) +
      geom_line () +
      labs(
        x = "Day",
        y = name_y_axis_total_bioarea,
        fill = "System nr",
        color = "System nr",
        linetype = ""
      ) +
      scale_linetype_discrete(labels = c(name_MM,
                                         name_SL)) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom"
      ) +
      scale_x_continuous(breaks = unique(ds_metaecosystems$day)) +
      geom_vline(
        xintercept = resource_flow_days[1] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[2] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[3] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[4] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[5] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[6] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      labs(caption = caption_resource_flow)
```

```{r}
p_boxplots = ds_metaecosystems %>%
      filter(disturbance == disturbance_input,
             metaecosystem_type %in% c("S_L", "M_M")) %>%
      ggplot (
        aes(
          x = day,
          y = total_metaecosystem_bioarea,
          group = interaction(day, metaecosystem_type),
          fill = metaecosystem_type
        )
      ) +
      geom_boxplot() +
      labs(
        x = "Day",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom"
      )  +
      scale_x_continuous(breaks = unique(ds_metaecosystems$day)) +
      geom_vline(
        xintercept = resource_flow_days[1] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[2] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[3] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[4] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[5] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      geom_vline(
        xintercept = resource_flow_days[6] + 0.7,
        linetype = "dotdash",
        color = "grey",
        size = 0.7
      ) +
      labs(caption = caption_resource_flow)

p_boxplots
```

```{r}
filtered_data = ds_metaecosystems %>%
    filter(metaecosystem_type %in% c("M_M", "S_L"),
           disturbance == disturbance_input,
           time_point >= first_time_point_model,
           time_point <= last_time_point_model)
```

```{r}
full_model = lmer(
  total_metaecosystem_bioarea ~
    day +
    metaecosystem_type +
    metaecosystem_type : day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

plot(full_model)
qqnorm(resid(full_model))

null_model = lmer(
  total_metaecosystem_bioarea ~
    day +
    (day | system_nr),
  data = filtered_data,
  REML = FALSE,
  control = lmerControl(optimizer = "Nelder_Mead")
)

AIC = AIC(full_model, null_model) #When I add baseline_bioarea : day, the AIC of the model stays the same when I take off the ecosystem type.

AIC

AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>Chisq)`[2]
p_value = round(p_value, digits = 3)
```

```{r}
p_boxplots + 
  labs(title = paste0("ΔAIC = ", deltaAIC , ", p = ", p_value))
```

##### Time point 1

Let's start by looking at whether meta-ecosystem type and disturbance had an effect at time point = 1. At this time point, no disturbance event had yet occurred. Therefore, we would not expect an effect of disturbance. In regards to meta-ecosystem type, there might be an effect if it comes from just the sizes of the two ecosystems.

```{r}
chosen_time_point = 1

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_1 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_1
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_1 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 2

```{r}
chosen_time_point = 2

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_2 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_2
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_2 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 3

```{r}
chosen_time_point = 3

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_3 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_3
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_3 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 4

```{r}
chosen_time_point = 4

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_4 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_4
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_4 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 5

```{r}
chosen_time_point = 5

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_5 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_5
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_5 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 6

```{r}
chosen_time_point = 6

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_6 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_6
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_6 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```

##### Time point 7

```{r}
chosen_time_point = 7

filtered_data = ds_metaecosystems %>%
                            filter(disturbance == disturbance_input,
                                   metaecosystem_type %in% c("M_M", "S_L"),
                                   time_point == chosen_time_point)

day_of_time_point = unique(filtered_data$day)
```

```{r}
time_point_7 = filtered_data %>%
      ggplot (aes(x = metaecosystem_type,
                  y = total_metaecosystem_bioarea)) +
      geom_boxplot() +
      labs(
        title = paste0(
          "Time point = ",
          chosen_time_point
        ),
        x = "",
        y = name_y_axis_total_bioarea,
        color = '',
        fill = ''
      ) +
      scale_fill_manual(
        values = c(colour_MM, colour_SL),
        labels = c(name_MM,
                   name_SL)
      ) +
      theme_bw() +
      theme(
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()
      )

time_point_7
```

```{r}

full_model = lm(total_metaecosystem_bioarea ~
            metaecosystem_type,
          data = filtered_data)

par(mfrow=c(2,3))
plot(full_model, which = 1:5)

null_model = lm(total_metaecosystem_bioarea ~
                  1,
          data = filtered_data)


AIC = AIC(full_model, null_model)
AIC
AIC_full = AIC$AIC[1]
AIC_null = AIC$AIC[2]
deltaAIC = AIC_full - AIC_null
deltaAIC = round(deltaAIC, digits = 2)

anova = anova(full_model, null_model)
anova

p_value = anova$`Pr(>F)`[2]
p_value = round(p_value, digits = 3)

R2_full = glance(full_model)$r.squared
R2_null = glance(null_model)$r.squared
R2_P =  R2_full - R2_null
R2_P = round(R2_P, digits = 2)
```

```{r}
time_point_7 +
  labs(
    title = paste0(
      "Day = ",
      day_of_time_point,
      ", ΔAIC = ",
      deltaAIC ,
      ", p = ",
      p_value,
      ", Adjusted R2 = ",
      R2_P
    )
  )
```