---
title: "PatchSizePilot"
author: "Emanuele Giacomuzzo"
date: "2022-08-03"
output: 
  html_document:
     code_folding: hide
bibliography: /Applications/Mendeley/library.bib
html_document:
    toc: true
    toc_float: true
    code_folding: hide
    number_sections: true
    includes:
      after_body: tabset-dropdown.html
editor_options: 
  chunk_output_type: console
---

```{r set-up-environment, echo = FALSE, results = FALSE, message = FALSE}
#renv::snapshot() #Run this to save all the current packages used in this project
rm( list = ls(  ) )
cat( "\014" )

start_time = Sys.time()

library("conflicted")
library("tidyverse")
library("grid")
library("gridExtra") 
library("lme4")
library("here")
library("MuMIn")
library("equatiomatic")
library("knitr")
library("optimx")
library("GenSA")
library("purrr")
library("kableExtra")
library("DT")
library("renv")
library("broom")
library("patchwork")
library("gganimate") 
library("gapminder")
library("gifski")
library("av")
#library("transformr") #Can't call it because sf package is not installed and when I try installing sf I get the error: configure: error: libproj or sqlite3 not found in standard or given locations. I'm for now not reinstalling it. I'll need it once that I update the body size gganimate plots. 
library("gifski")
library("GGally")
library("strengejacke")
library("sjPlot")
library("sjstats")

conflict_prefer("load", "base")
conflict_prefer("filter", "dplyr")

knitr::opts_chunk$set(message = FALSE)

source(here("r_files", "biomass", "functions", "biomass_plots.R"))
source(here("r_files", "biomass", "functions", "update_all_models_table.R"))
source(here("r_files", "body_size", "functions", "plot_data_mean.R"))
source(here("r_files", "body_size", "functions", "plot_data_raw.R"))

gif_figures = TRUE

p = NULL #To run the plotting function

#Publication settings
publication_width = 12
publication_height = 12
publication_unit = "cm"

first_perturbation_day = 5
```

# PatchSizePilot {.tabset}

## Biomass {.tabset .tabset-pills}

```{r child = here("r_files", "biomass", "main_biomass.Rmd")}
```

## Body size {.tabset .tabset-pills}

```{r child = here("r_files", "body_size", "main_body_size.Rmd")}
```

## Figures

```{r, echo = FALSE, fig.align='center', fig.cap = "Regional biomass production (mean bioarea density between two patches) in meta-ecosystems of the same total area, but whose two patches have either the same size or that have a smaller and larger patch. For clarity, only the low disturbance treatment is shown here. See the Appendix for equivalent the figure of the high disturbance treatment."}
p_regional_low_mean + labs(title = "")

ggsave(here("results", "biomass", "publication_regional_low_mean.jpg"), 
       p_regional_low_mean + labs(title = ""), 
       units = publication_unit,
       width = publication_width, 
       height = publication_height)
```

```{r, echo = FALSE, fig.align = 'center', fig.cap = "Local biomass production (bioarea density) in patches that are either isolated, connnected to a patch of the same size or to a patch of a larger size. For clarity, only the low disturbance treatment is shown here. See the Appendix for equivalent the figure of the high disturbance treatment."}
local_small_low_plot + labs(title = "")

ggsave(here("results", "biomass", "publication_local_small_low_plot.jpg"), 
       local_small_low_plot + labs(title = ""), 
       units = publication_unit,
       width = publication_width, 
       height = publication_height)
```

```{r, echo = FALSE, fig.align = 'center', fig.cap = "Local biomass production in patches that are either isolated, connected to the same size, or connected to a smaller size. For clarity, only the high disturbance treatment is shown here. See the Appendix for equivalent the figure of the low disturbance treatment."}
local_large_high_plot + labs(title = "")

ggsave(here("results", "biomass", "publication_local_small_low_plot.jpg"), 
       local_large_high_plot + labs(title = ""), 
       units = publication_unit,
       width = publication_width, 
       height = publication_height)
```

```{r, fig.align = 'center', fig.cap="Small patches this time in logRR"}
small_patches_figure + labs(title = "")
```

## Tests

```{r child = here("r_files", "tests", "evaporation_tests.Rmd")}
```

## Running time

```{r running-time, echo = FALSE, eval = TRUE}
end_time = Sys.time()
end_time - start_time
```

## Other

### Mixed effects models

-   To build the mixed effect models we will use the R package lme4. See page 6 of [this PDF](https://cran.r-project.org/web/packages/lme4/vignettes/lmer.pdf) to know more about the syntaxis of this package.

-   To do model diagnostics of mixed effect models, I'm going to look at the following two plots (as suggested by @Zuur2009, page 487):

    -   Quantile-quantile plots

    -   Partial residual plots

-   The effect size of the explaining variables is calculated in the mixed effect models as marginal and conditional r squared. The marginal r squared is how much variance is explained by the fixed effects. The conditional r squared is how much variance is explained by the fixed and the random effects. The marginal and conditional r squared are calculated using the package `MuMIn`. The computation is based on the methods of @Nakagawa2017. For the coding and interpretation of these r squared check the [documentation for the r.squaredGLMM function](https://rdrr.io/cran/MuMIn/man/r.squaredGLMM.html)

-   See for the interaction syntaxis [this link.](https://mspeekenbrink.github.io/sdam-r-companion/linear-mixed-effects-models.html)

### Model selection

-   I am starting from the largest model and then simplifying because ... (see statistical modelling course at ETH).

-   I am going to select the best model according to AIC. BIC is better for understanding and AIC for predicting. @Halsey2019 also suggests this approach instead of p values. I'm going to use AIC because I'm interested in knowing how much meta-ecosystem type contributed to the overall regional biomass.

## Bibliography

```{r extract-sections, echo = FALSE, eval = FALSE}
#You can just run this to run all the sections so then you can work on them. 

library(here)
library(knitr)
for (main_section in c("biomass", "body_size")){
  
 sections.path = here("r_files", main_section, "sections")
 extracted.path = here("r_files", main_section, "extracted_sections")
 
 r.files = list.files(sections.path)
 rmd.files = r.files[grepl(".Rmd", r.files)]
 
 
 map(rmd.files, function(file.i) {
   
   file.name = gsub(".Rmd", "", file.i)
   extracted.file = paste0(file.name, ".R")
   purl(file.path(sections.path, file.i),
        file.path(extracted.path, extracted.file))}) 
}
```
