---
title: "parameters"
output: html_document
date: "2023-02-08"
editor_options: 
  chunk_output_type: console
---

Parameters for R markdown and the general running of the code.

```{r}
start_time = Sys.time()
knitr::opts_chunk$set(message = FALSE,
                      cache = FALSE,
                      autodep = FALSE)
recompute_lengthy_analyses = FALSE 
```

Parameters related to resource flows.

```{r}
disturbance_levels = c("low", "high")
n_disturbance_levels = length(disturbance_levels)

resource_flow_days = c(5, 9, 13, 17, 21, 25)
first_resource_flow = resource_flow_days[1]
```

Parameters related to sampling.

```{r}
total_frames = 125
volume_recorded_μl = 34.4
time_points = 0:7
time_points_without_t0 = 1:7
time_point_names = c("t0", "t1", "t2", "t3", "t4", "t5", "t6", "t7")
sampling_days = c(0, 4, 8, 12, 16, 20, 24, 28)
first_time_point = 0
last_time_point = length(sampling_days) - 1
n_time_points = last_time_point + 1
nr_videos = c(12, 1, 1, 1, 1, 1, 2, 2) #Videos taken for each time point for each culture. At t0 we took 12 videos of the large bottle from which we started the  cultures. Write why 2 at the end. 

videos_taken = data.frame(time_point = 0 : 7,
                          nr_videos = c(12, 1, 1, 1, 1, 1, 2, 2))

n_videos_taken_t0 = nr_videos[1]

time_point_day = data.frame(time_point = first_time_point:last_time_point,
                            day = sampling_days,
                            video_replicates = nr_videos)

videos_to_take_off = data.frame(culture_ID = NA,
                                time_point = NA,
                                file = NA) %>%
                     add_row(culture_ID = 137-110, 
                             time_point = 7, 
                             file = 137) %>%
                     slice(-1)

n_cultures = 110
total_number_of_video_rows = sum(nr_videos * n_cultures)
```

Parameters related to protists.

```{r}
protist_species = c("Ble", "Cep", "Col", "Eug", "Eup", "Lox", "Pau", "Pca", "Spi", "Spi_te", "Tet")
protist_species_indiv_per_volume = paste0(protist_species, "_indiv_per_volume")
protist_species_indiv_per_ml = paste0(protist_species, "_indiv_per_ml")
protist_species_dominance = paste0(protist_species_indiv_per_ml, "_dominance")
protist_species_total = paste0(protist_species, "_tot_indiv")
n_protist_species = length(protist_species)
first_protist = protist_species[1]
last_protist = protist_species[n_protist_species]
species_IDD_with_13_threshold = c("Col", "Eug", "Eup", "Lox", "Pau", "Pca", "Spi_te", "Tet")
species_IDD_with_13_threshold_indiv_per_volume = paste0(species_IDD_with_13_threshold, "_indiv_per_volume")
species_IDD_with_40_threshold = c("Ble", "Cep", "Spi")
species_IDD_with_40_threshold_indiv_per_volume = paste0(species_IDD_with_40_threshold, "_indiv_per_volume")
```

Parameters related to patches.

```{r}
patches_to_take_off = 60 #Culture ID = 60 as it was spilled (small unconnected, high disturbance, system nr = 40)
culture_info = read.csv(here("data", "culture_info.csv"), header = TRUE)

columns_patches = c("time_point",
                    "day",
                    "culture_ID",
                    "system_nr",
                    "disturbance",
                    "patch_type",
                    "patch_size",
                    "patch_size_ml",
                    "size_connected_patch",
                    "metaecosystem",
                    "metaecosystem_type")
columns_treatments = columns_patches[!columns_patches %in% c("system_nr", "culture_ID")]

variables_patches = c("bioarea_mm2_per_ml",
                      "bioarea_tot_mm2",
                      "indiv_per_ml",
                      "indiv_tot",
                      "species_richness",
                      "shannon",
                      "simpson",
                      "inv_simpson",
                      "evenness_pielou",
                      "median_body_area_µm2",
                      paste0(protist_species, "_indiv_per_ml"),
                      paste0(protist_species, "_tot_indiv"),
                      paste0(protist_species_indiv_per_ml, "_dominance"))
baseline_columns = paste0("baseline_", variables_patches)

patch_types_ordered = c("Small connected to large",
                        "Small connected to small",
                        "Small unconnected",
                        "Medium connected to medium",
                        "Medium unconnected",
                        "Large connected to small",
                        "Large connected to large",
                        "Large unconnected")

treatments_and_controls = data.frame(treatment = c("Small connected to small",
                                                   "Small connected to large",
                                                   "Medium connected to medium",
                                                   "Large connected to large",
                                                   "Large connected to small"),
                                     control = c("Small unconnected",
                                                 "Small unconnected",
                                                 "Medium unconnected",
                                                 "Large unconnected",
                                                 "Large unconnected"))

n_treatments = length(unique(treatments_and_controls$treatment))
n_controls = length(unique(treatments_and_controls$control))
n_replicates = 5
n_patch_types = 8
```

Parameters related to size classes.

```{r}
n_size_classes = 12
columns_classes = c(columns_patches,
                    "size_class_n",
                    "mean_class_area_µm2")
```

Parameters related to meta-ecosystems.

```{r}
metaecosystems_to_take_off = culture_info %>%
  filter(culture_ID %in% patches_to_take_off) %>%
  pull(system_nr) %>%
  unique

system_nr_metaecosystems = culture_info %>%
  filter(metaecosystem == "yes") %>%
  pull(system_nr) %>%
  unique

n_metaecosystems = length(system_nr_metaecosystems)

variables_metaecos = c(
  "total_metaecosystem_bioarea_mm2",
  "jaccard_index",
  "bray_curtis",
  "beta_spatial_turnover",
  "beta_nestedness",
  "beta_total",
  "metaecosystem_richness")

metaecosystem_types_ordered = c(
      "Small-Small meta-ecosystem",
      "Medium-Medium meta-ecosystem",
      "Medium-Medium unconnected",
      "Large-Large meta-ecosystem",
      "Small-Large meta-ecosystem",
      "Small-Large unconnected")
```

Name of the axes per response variable.

```{r}
axis_names = data.frame(variable = NA,
                        axis_name= NA) %>%
  add_row(variable = "day", axis_name = "Time (day)") %>%
  add_row(variable = "patch_size_ml", axis_name = "Patch size (ml)") %>%
  add_row(variable = "log_size_class", axis_name = "Log size (μm2)") %>%
  add_row(variable = "class_indiv_per_µl", axis_name = "Density (ind/ml)") %>%
  add_row(variable = "bioarea_mm2_per_ml", axis_name = "Biomass (mm2/ml)") %>%
  add_row(variable = "bioarea_mm2_per_ml_d", axis_name = "Bioamass ES") %>%
  add_row(variable = "bioarea_tot", axis_name = "Tot Biomass (mm2)") %>%
  add_row(variable = "total_metaecosystem_bioarea_mm2", axis_name = "Tot Biomass (mm2)") %>%
  add_row(variable = "species_richness", axis_name = "Species Richness") %>%
  add_row(variable = "species_richness_d", axis_name = "Species Richness ES") %>%
  add_row(variable = "mean_richness", axis_name = "mean α Diversity (Shannon)") %>%
  add_row(variable = "mean_shannon", axis_name = "mean α Diversity (Shannon)") %>%
  add_row(variable = "shannon", axis_name = "Biodiversity (Shannon)") %>%
  add_row(variable = "shannon_d", axis_name = "Biodiversity ES (Shannon ES)") %>%
  add_row(variable = "bray_curtis", axis_name = "β Diversity (Bray-Curtis)") %>%
  add_row(variable = "beta_spatial_turnover", axis_name = "Turn over (Simpson pair-wise dissimilarity)") %>%
  add_row(variable = "beta_nestedness", axis_name = "Nestedness (nestedness-fraction of Sorensen)") %>%
  add_row(variable = "beta_total", axis_name = "Tot β Diversity (Sorensen)") %>%
  add_row(variable = "metaecosystem_richness", axis_name = "γ Diversity (Species Richness)") %>%
  add_row(variable = "indiv_per_ml", axis_name = "Abundance (ind/ml)") %>%
  add_row(variable = "indiv_per_ml_d", axis_name = "Abundance ES") %>%
  add_row(variable = "median_body_area_µm2", axis_name = "Median body size (µm²)") %>%
  add_row(variable = "median_body_area_µm2_d", axis_name = "Median Body Size ES") %>%
  add_row(variable = "Ble_indiv_per_ml", axis_name = "Ble Density (ind/ml)") %>% 
  add_row(variable = "Cep_indiv_per_ml", axis_name = "Cep Density (ind/ml)") %>%
  add_row(variable = "Col_indiv_per_ml", axis_name = "Col Density (ind/ml)") %>%
  add_row(variable = "Eug_indiv_per_ml", axis_name = "Eug Density (ind/ml)") %>%
  add_row(variable = "Eup_indiv_per_ml", axis_name = "Eup Density (ind/ml)") %>%
  add_row(variable = "Lox_indiv_per_ml", axis_name = "Lox Density (ind/ml)") %>%
  add_row(variable = "Pau_indiv_per_ml", axis_name = "Pau Density (ind/ml)") %>%
  add_row(variable = "Pca_indiv_per_ml", axis_name = "Pca Density (ind/ml)") %>%
  add_row(variable = "Spi_indiv_per_ml", axis_name = "Spi Density (ind/ml)") %>%
  add_row(variable = "Spi_te_indiv_per_ml", axis_name = "Spi te Density (ind/ml)") %>%
  add_row(variable = "Tet_indiv_per_ml", axis_name = "Tet Density (ind/ml)") %>%
  add_row(variable = "auto_hetero_ratio", axis_name = "Autotrophic/Heterotrophic individuals ratio") %>%
  add_row(variable = "Ble_indiv_per_ml_d", axis_name = "Ble Density ES") %>%
  add_row(variable = "Cep_indiv_per_ml_d", axis_name = "Cep Density ES") %>%
  add_row(variable = "Col_indiv_per_ml_d", axis_name = "Col Density ES") %>%
  add_row(variable = "Eug_indiv_per_ml_d", axis_name = "Eug Density ES") %>%
  add_row(variable = "Eup_indiv_per_ml_d", axis_name = "Eup Density ES") %>%
  add_row(variable = "Lox_indiv_per_ml_d", axis_name = "Lox Density ES") %>%
  add_row(variable = "Pau_indiv_per_ml_d", axis_name = "Pau Density ES") %>%
  add_row(variable = "Pca_indiv_per_ml_d", axis_name = "Pca Density ES") %>%
  add_row(variable = "Spi_indiv_per_ml_d", axis_name = "Spi Density ES") %>%
  add_row(variable = "Spi_te_indiv_per_ml_d", axis_name = "Spi te Density ES") %>%
  add_row(variable = "Tet_indiv_per_ml_d", axis_name = "Tet Density ES") %>%
  add_row(variable = "Ble_indiv_per_ml_dominance", axis_name = "Ble Dominance (%)") %>%
  add_row(variable = "Cep_indiv_per_ml_dominance", axis_name = "Cep Dominance (%)") %>%
  add_row(variable = "Col_indiv_per_ml_dominance", axis_name = "Col Dominance (%)") %>%
  add_row(variable = "Eug_indiv_per_ml_dominance", axis_name = "Eug Dominance (%)") %>%
  add_row(variable = "Eup_indiv_per_ml_dominance", axis_name = "Eup Dominance (%)") %>%
  add_row(variable = "Lox_indiv_per_ml_dominance", axis_name = "Lox Dominance (%)") %>%
  add_row(variable = "Pau_indiv_per_ml_dominance", axis_name = "Pau Dominance (%)") %>%
  add_row(variable = "Pca_indiv_per_ml_dominance", axis_name = "Pca Dominance (%)") %>%
  add_row(variable = "Spi_indiv_per_ml_dominance", axis_name = "Spi Dominance (%)") %>%
  add_row(variable = "Spi_te_indiv_per_ml_dominance", axis_name = "Spi te Dominance (%)") %>%
  add_row(variable = "Tet_indiv_per_ml_dominance", axis_name = "Tet Dominance (%)") %>%
  add_row(variable = "Ble_indiv_per_ml_dominance_d", axis_name = "Ble Dominance ES") %>%
  add_row(variable = "Cep_indiv_per_ml_dominance_d", axis_name = "Cep Dominance ES") %>%
  add_row(variable = "Col_indiv_per_ml_dominance_d", axis_name = "Col Dominance ES") %>%
  add_row(variable = "Eug_indiv_per_ml_dominance_d", axis_name = "Eug Dominance ES") %>%
  add_row(variable = "Eup_indiv_per_ml_dominance_d", axis_name = "Eup Dominance ES") %>%
  add_row(variable = "Lox_indiv_per_ml_dominance_d", axis_name = "Lox Dominance ES") %>%
  add_row(variable = "Pau_indiv_per_ml_dominance_d", axis_name = "Pau Dominance ES") %>%
  add_row(variable = "Pca_indiv_per_ml_dominance_d", axis_name = "Pca Dominance ES") %>%
  add_row(variable = "Sp_indiv_per_mli_dominance_d", axis_name = "Spi Dominance ES") %>%
  add_row(variable = "Spi_te_indiv_per_ml_dominance_d", axis_name = "Spi te Dominance ES") %>%
  add_row(variable = "Tet_indiv_per_ml_dominance_d", axis_name = "Tet Dominance ES") %>%
  add_row(variable = "dominance", axis_name = "Dominance (%)") %>%
  add_row(variable = "log_abundance", axis_name = "Log Abundance + 1 (ind/mm²)") %>%
  add_row(variable = "abundance_hedges_d", axis_name = "Density ES") %>%
  add_row(variable = "beta_diversity_from_unconnected", axis_name = "Divergence from unconnected") %>%
  add_row(variable = "beta_diversity_from_previous_time", axis_name = "Temporal Divergence") %>%
  add_row(variable = "beta_diversity_from_previous_time_d", axis_name = "Temporal Divergence ES") %>%
  add_row(variable = "evenness_pielou", axis_name = "Evenness") %>%
  add_row(variable = "evenness_pielou_d", axis_name = "Evenness ES") %>%
  slice(-1)
```

Colour and line type per ecosystem/meta-ecosystem type.

```{r}
parameters_treatments = data.frame(treatment = NA,
                                colour = NA,
                                linetype = NA) %>%
  add_row(treatment = "Small connected to large", colour = "#feb24c", linetype = "solid") %>%
  add_row(treatment = "Small connected to small", colour = "#feb24c", linetype = "dashed") %>%
  add_row(treatment = "Small unconnected", colour = "#bdbdbd", linetype = "solid") %>% 
  add_row(treatment = "Large connected to small", colour = "#3182bd", linetype = "solid") %>%
  add_row(treatment = "Large connected to large", colour = "#3182bd", linetype = "dashed") %>%
  add_row(treatment = "Large unconnected", colour = "#000000", linetype = "solid") %>%
  add_row(treatment = "Medium connected to medium", colour = "#de2d26", linetype = "solid") %>%
  add_row(treatment = "Medium unconnected", colour = "#737373", linetype = "solid") %>%
  add_row(treatment = "Small-Large meta-ecosystem", colour = "#762a83", linetype = "solid") %>%
  add_row(treatment = "Small-Large unconnected", colour = "#762a83", linetype = "dashed") %>%
  add_row(treatment = "Medium-Medium meta-ecosystem", colour = "#1b7837", linetype = "solid") %>%
  add_row(treatment = "Medium-Medium unconnected", colour = "#1b7837", linetype = "dashed") %>%
  add_row(treatment = "Large-Large meta-ecosystem", colour = "#67000d", linetype = "solid") %>%
  add_row(treatment = "Small-Small meta-ecosystem", colour = "#fc9272", linetype = "solid") %>%
  slice(-1)
```

Parameters for plotting.

```{r}
figures_height_rmd_output = 7

legend_position = "top"
legend_width_cm = 2
size_legend = 12
size_x_axis = 13
size_y_axis = size_x_axis
boxplot_width = 2
dodging = 0.5 
width_errorbar = 0.2
dodging_error_bar = 0.5

treatment_lines_linewidth = 1
treatment_points_size = 2.5

resource_flow_line_type = "solid"
resource_flow_line_colour = "#d9d9d9"
resource_flow_line_width = 0.3

zero_line_colour = "grey"
zero_line_line_type = "dotted"
zero_line_line_width = 0.5
zero_line_ES_line_type = "dotted"
zero_line_ES_colour = "grey"
zero_line_ES_line_width = 1

ggarrange_margin_top = 0
ggarrange_margin_bottom = 0
ggarrange_margin_left = 0
ggarrange_margin_right = 0

paper_width = 17.3
paper_height = 20
paper_units = "cm"
paper_res = 600
paper_y_axis_size = 9

presentation_figure_size = 15
presentation_figure_width = 30
presentation_figure_height = 22
presentation_legend_size = 20
presentation_x_axis_size = 22
presentation_y_axis_size = presentation_x_axis_size
presentation_axes_size = 12
presentation_treatment_points_size = 5
presentation_treatment_linewidth = 2
presentation_figure_units = "cm"
presentation_figure_res = 600

grey_background_xmin = -Inf
grey_background_xmax = 7.5
grey_background_ymin = -Inf
grey_background_ymax = Inf
grey_background_fill = "#f0f0f0"
grey_background_alpha = 0.03
grey_background_color = "transparent"
```

Parameters for modelling.

```{r modeling_parameters}
first_time_point_model = 2 #Time point 2 is the first after disturbance
last_time_point_model = last_time_point

optimizer_input = 'Nelder_Mead'
method_input = ''

compar_ex = "The full and fixed models are compared to the null model."

results_table = data.frame(Response = as.character(NA),
                           Levels = as.character(NA),
                           ΔAIC_full = NA,
                           p_full = NA,
                           ΔR2_full = NA,
                           ΔAIC_fix = NA,
                           p_fix = NA,
                           ΔR2_fix = NA) %>%
  slice(-1)
```